---
title: "10_glmnet_1siq_loocv_analysis"
author: "Jackie"
date: "10/26/2020"
output:
  word_document: default
  html_notebook: default
  html_document:
    df_print: paged
---

```{r, message=FALSE}
library(glmnet)
library(glmpath)
library(lars)
library(tidyverse)
library(dynutils)
library(readxl)
library(haven)
library(naniar)
library(pscl)
library(MASS)
library(stringr)
library(sjPlot)
library(directlabels)
library(caret)

set.seed(1234)
```

```{r, message=FALSE}
graph_net_fp <- "~/Box/Mooddata_Coordinating/1_Lab_Coordinating/Users/JackieSchwartz/PHIND_RS_and_Suicide/Octo2020Analysis/siq_graph.csv"

graph_net <- read_csv(graph_net_fp)
```

```{r}
options(scipen=999) 
z_score <- function(x) {
diff_mu <- x - mean(x, na.rm = T)
sd <- sd(x, na.rm = T)
diff_mu / sd
}
```

## de-selecting variables
```{r}
graph_net_select <- graph_net %>%
  dplyr::select(-c(siq_total.T3, T3_YSR_old_Internalizing_Problems_Total_Score, meds_baseline, T1_KSADS_C_or_P_Thoughts, T1_KSADS_C_or_P_bx, Age_S1.T3, Tanner_Average.T3))

# already filtered out those with history of stbs
```

#### recoding and standardizing
```{r}

graph_net_stand <- graph_net_select %>%
  # converting race/ethinicity to factor and binarizing for analysis
  mutate(
    KSADS_Child_Race_by_P.T1 = factor(KSADS_Child_Race_by_P.T1),
    KSADS_Child_Race_by_P.T1_bin = ifelse(KSADS_Child_Race_by_P.T1 == "1", "1", "0"),
    # converting sex and sleepiness to factor
    sex_child = factor(sex_child),
    sex_child = ifelse(sex_child == "2", "1", "0"),
    sleepy = factor(sleepy),
    ) %>%
  # z-scoring siq (doing this separately so I can append a z to it as my DV)
  mutate(siq_total_log_z = z_score(siq_total_log)) %>%
  # removing orig race/ethnicity and siq log variable
  dplyr::select(-KSADS_Child_Race_by_P.T1, -siq_total_log) %>%
  # z-scoring all numeric variables
  mutate_at(vars(-ELS_ID, -siq_total_log_z, -KSADS_Child_Race_by_P.T1_bin, -sex_child, -sleepy), z_score) %>%
  # arranging with ELS_ID first, then siq, then everything else
  dplyr::select(ELS_ID, siq_total_log_z, everything())


graph_net_stand_fp <- "~/Box/Mooddata_Coordinating/1_Lab_Coordinating/Users/JackieSchwartz/PHIND_RS_and_Suicide/Octo2020Analysis/siq_graph_net_stand.csv"

graph_net <- write_csv(graph_net_stand, graph_net_stand_fp)
```


```{r}
graph_net_stand <-
  graph_net_stand %>%
  mutate_at(vars(KSADS_Child_Race_by_P.T1_bin, sex_child, sleepy), factor)
contrasts(graph_net_stand$KSADS_Child_Race_by_P.T1_bin) = contr.treatment(2)
contrasts(graph_net_stand$sex_child) = contr.treatment(2)
contrasts(graph_net_stand$sleepy) = contr.treatment(2)
```

```{r}
supp_graph_net_stand_siq <- graph_net_stand %>%
  dplyr::select(-ELS_ID) %>%
  dplyr::select(siq_total_log_z, everything()) # response (dv) variable in first column

#as.matrix
supp_predictors_scaled <- data.matrix(supp_graph_net_stand_siq[2:1263]) # columns 2 - 1263 are predictors
supp_siq_scaled <-supp_graph_net_stand_siq$siq_total_log_z # my response variable
```

## to get sense of coefficient path
```{r}
# if i want to UN-penalize variable (e.g., framewise displacement)
# supp_p.fac = rep(1, 1259)
# supp_p.fac[c(1259)] = 0

supp_lasso <- glmnet(supp_predictors_scaled, supp_siq_scaled, family = "gaussian", alpha = 1)

plot(supp_lasso, xvar = "dev", label = TRUE)
```

okkayy so seems like 80/20 split on such a small sample is not wise. After speaking with Trevor H. suggested LOOCV, which actually minimizes simulation error and bias (avoiding randomness in the fold), and you're predicting the observation that wasn't used to fit the model.

### setting up folds
```{r}
set.seed(1234)
# We will use LOOCV to avoid randomness in folds

k <- supp_graph_net_stand_siq %>% nrow() # k is equal to num of obs
k
```


```{r}
# conducting cross validated glmnet on whole sample using LOOCV
cv_model_loocv <- cv.glmnet(x = supp_predictors_scaled,
                            y = supp_siq_scaled,
                            standardize = FALSE, # already scaled
                            family = "gaussian",
                            grouped = FALSE,
                            nfolds = k)

# computing RSquared value
# supp_predictors_scaled is my x matrix
# supp_siq_scaled is my y
X <- model.matrix(siq_total_log_z ~ ., data = supp_graph_net_stand_siq)[,-1]
# predict
y_hat <- predict(cv_model_loocv,  newx = X,  s = "lambda.min")
# R-Squared
r_sq <- 1 - (sum((supp_siq_scaled - y_hat)^2) / sum((supp_siq_scaled - mean(supp_siq_scaled))^2))
r_sq # 0.2259336


## extracting coefficients
cv_model_loocv$lambda.min # 0.1841177
options(max.print = 1265)
coef_loocv <- coef(cv_model_loocv, s = "lambda.min")
```

### plotting the loocv lasso coefficients
```{r}
siq_loocv_lasso_coef <- read_excel("tbl3toPlot.xlsx", sheet = "siq")
```

```{r}
siq_lasso_results <- siq_loocv_lasso_coef %>%
  ggplot(
    aes(
      x = reorder(Variables, sibetavalue),
      y = sibetavalue,
      fill = `Participant Characteristic / Brain Region`
    )
  ) + 
  scale_y_continuous(breaks = seq(-.10, .15, by = .01)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(x = "Variables", y = expression(beta)) +
  ggtitle("Predictors of Severity of Suicidal Ideation") +
  theme_blank() +
  theme(axis.text.x = element_text(size = 8, angle = 90, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        legend.text = element_text(size = 8, color = "black"),
        legend.title = element_text(size = 10, color = "black")) +
  scale_fill_manual(values = c("Participant Characteristic" = "cornflowerblue",
                               "Frontal Gyrus" = "violet",
                               "Temporal Gyrus" = "gold1",
                               "Basal Ganglia" = "mediumseagreen",
                               "Cingulate Gyrus" = "darkorange",
                               "Parietal Lobe" = "turquoise",
                               "Subcortical Nuclei" = "purple"))

ggsave("siq_lasso_results.jpg", siq_lasso_results, width = 10, height = 5)
```

