---
title: "10_glmnet_ysr_nest_resamp"
author: "Jackie"
date: "5/16/21"
output: html_notebook
---


This script performs nested resampling using loocv on inner and outer resamples to obtain relavtively unbiased performance estimation

# loading libraries
```{r, message=FALSE}
library(glmnet)
library(lars)
library(tidyverse)
library(readxl)
library(pscl)
library(MASS)
library(stringr)
library(sjPlot)
library(directlabels)
library(paradox)
library(mlr)

# set seed
set.seed(1234)

# expanding print
options(max.print = 1275)
```

# reading in data
```{r, message=FALSE}
graph_net_fp <- "~/Box/Mooddata_Coordinating/1_Lab_Coordinating/Users/JackieSchwartz/PHIND_RS_and_Suicide/April2021Analysis/fmaps_and_nofmaps/siq_graph.csv"

graph_net <- read_csv(graph_net_fp)
```


# function to z-score
```{r}
options(scipen=999) 
z_score <- function(x) {
diff_mu <- x - mean(x, na.rm = T)
sd <- sd(x, na.rm = T)
diff_mu / sd
}
```

## de-selecting variables
```{r}
graph_net_select_brain <- graph_net %>%
  dplyr::select(
    -c(meds_baseline)
    )
# already filtered out those with history of stbs
```

#### recoding and standardizing
```{r}
graph_net_stand_brain <- graph_net_select_brain %>%
  # converting race/ethinicity to factor and binarizing for analysis
  mutate(
    KSADS_Child_Race_by_P.T1 = factor(KSADS_Child_Race_by_P.T1),
    KSADS_Child_Race_by_P.T1_bin = ifelse(KSADS_Child_Race_by_P.T1 == "1", "1", "0"),
    # 1 = white, 0 = poc
    # converting sex and sleepiness to factor
    sex_child = factor(sex_child),
    sex_child = ifelse(sex_child == "2", "1", "0"),
    sleepy = factor(sleepy),
    fmap_applied = factor(fmap_applied)
    ) %>%
  dplyr::select(-KSADS_Child_Race_by_P.T1, -siq_total.T3) %>%
  # z-scoring all numeric variables
  mutate_at(vars(-ELS_ID, -siq_total_log, -KSADS_Child_Race_by_P.T1_bin, -sex_child, -sleepy, -fmap_applied, -T3_ysr_internalizing_sum), z_score) %>%
  # arranging with ELS_ID first, then siq, then everything else
  mutate(siq_total_log_z = z_score(siq_total_log),
         T3_ysr_internalizing_sum_z = z_score(T3_ysr_internalizing_sum)) %>%
  dplyr::select(ELS_ID, T3_ysr_internalizing_sum_z, T3_ysr_internalizing_sum, siq_total_log_z, siq_total_log, everything())

# mean(graph_net_stand_brain$fmap_applied == "1")

graph_net_stand_fp <- "~/Box/Mooddata_Coordinating/1_Lab_Coordinating/Users/JackieSchwartz/PHIND_RS_and_Suicide/April2021Analysis/fmaps_and_nofmaps/ysr_graph_net_stand_brainmod.csv"

graph_net <- write_csv(graph_net_stand_brain, graph_net_stand_fp)
```

#### setting contrasts
```{r}
graph_net_stand_brain <-
  graph_net_stand_brain %>%
  mutate_at(vars(KSADS_Child_Race_by_P.T1_bin, sex_child, sleepy, fmap_applied), factor)
contrasts(graph_net_stand_brain$KSADS_Child_Race_by_P.T1_bin) = contr.treatment(2)
contrasts(graph_net_stand_brain$sex_child) = contr.treatment(2)
contrasts(graph_net_stand_brain$sleepy) = contr.treatment(2)
contrasts(graph_net_stand_brain$fmap_applied) = contr.treatment(2)
```

#### constructing x matrix and y vector
```{r}
graph_net_stand_siq_brain <- graph_net_stand_brain %>%
  dplyr::select(-ELS_ID, -siq_total_log, -T3_ysr_internalizing_sum) %>%
  dplyr::select(T3_ysr_internalizing_sum_z, siq_total_log_z, everything()) # response (dv) variable in first column

#as.matrix
predictors_ysr_scaled_brain <- data.matrix(graph_net_stand_siq_brain[2:1271]) # columns 2 - 1271 are predictors
ysr_scaled_brain <- graph_net_stand_siq_brain$T3_ysr_internalizing_sum_z # my response variable
save(predictors_ysr_scaled_brain, file = "predictors_ysr_scaled_brain.rda")
save(ysr_scaled_brain, file = "ysr_scaled_brain.rda")
```

## to get sense of coefficient path
```{r}
lasso_ysr_brain <- glmnet(predictors_ysr_scaled_brain, ysr_scaled_brain, family = "gaussian", alpha = 1, standardize = FALSE)
# 
plot(lasso_ysr_brain, xvar = "dev", label = TRUE)
```
# nested cv
```{r}
library(remotes)
n <- 106

## Your procedure

cvfit <- cv.glmnet(predictors_ysr_scaled_brain, ysr_scaled_brain, standardize = FALSE, alpha = 1, nfolds = n)
betas <- coef(cvfit, s = "lambda.min")

# computing rsquared of unnested cv
X <- model.matrix(T3_ysr_internalizing_sum_z ~ ., data = graph_net_stand_siq_brain)[,-1]
# predict
y_hat <- predict(cvfit,  newx = X,  s = "lambda.min")
# R-Squared
r_sq <- 1 - (sum((ysr_scaled_brain - y_hat)^2) / sum((ysr_scaled_brain - mean(ysr_scaled_brain))^2))
r_sq # 0.6116964 standardized prior to glmnet
cvfit$lambda.min # 0.1487689

## Get measure of performance of procedure
preds <- double(n)
ybars <- double(n)
for(i in 1:n){
    cvfit.inner <- cv.glmnet(predictors_ysr_scaled_brain[-i,], ysr_scaled_brain[-i], standardize = FALSE, nfolds = n-1, grouped=FALSE, alpha=1)
    preds[i] <- predict(cvfit.inner, newx = predictors_ysr_scaled_brain[i,,drop=FALSE], s = "lambda.min")
    ybars[i] <- mean(ysr_scaled_brain[-i])
    cat(i)
}

# total SS
mse0 <- mean((ysr_scaled_brain-ybars)^2) # 1.009524
# mean square error
mse <- mean((ysr_scaled_brain-preds)^2) # 0.5806678

R2 <-1- mse/mse0 # 0.4248102
```

# zero-order correlations

```{r}
graph_net_corr <- graph_net_select_brain %>%
  # converting race/ethinicity to factor and binarizing for analysis
  mutate(
    KSADS_Child_Race_by_P.T1 = factor(KSADS_Child_Race_by_P.T1),
    KSADS_Child_Race_by_P.T1_bin = ifelse(KSADS_Child_Race_by_P.T1 == "1", "1", "0"),
    # converting sex and sleepiness to factor
    sex_child = factor(sex_child),
    sex_child = ifelse(sex_child == "2", "1", "0"),
    sleepy = factor(sleepy),
    fmap_applied = factor(fmap_applied)
    ) %>%
  dplyr::select(ELS_ID, T3_ysr_internalizing_sum, siq_total_log, everything())
graph_net_corr <-
  graph_net_corr %>%
  mutate_at(vars(KSADS_Child_Race_by_P.T1_bin, sex_child, sleepy, fmap_applied), factor)
contrasts(graph_net_corr$KSADS_Child_Race_by_P.T1_bin) = contr.treatment(2)
contrasts(graph_net_corr$sex_child) = contr.treatment(2)
contrasts(graph_net_corr$sleepy) = contr.treatment(2)
contrasts(graph_net_corr$fmap_applied) = contr.treatment(2)
```


```{r}
labeltheme <- theme(axis.title.y = element_blank(),
                    text = element_text(size = 7))
# internalizing at follow-up
cor.test(graph_net_corr$siq_total_log, graph_net_corr$T3_ysr_internalizing_sum)
si_cor <-
  graph_net_corr %>%
  ggplot(
    aes(
      x = siq_total_log, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Concurrent Suicidal Ideation Severity"
  ) +
  labeltheme
si_cor

# externalizing at follow-up
cor.test(graph_net_corr$T3_ysr_internalizing_sum, graph_net_corr$T3_ysr_externalizing_sum)
externalizing_cor <-
  graph_net_corr %>%
  ggplot(
    aes(
      x = T3_ysr_externalizing_sum, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Concurrent Externalizing Severity"
  ) +
  labeltheme
externalizing_cor

# degree of Temporal agranular insular parahippocampal gyrus (L) (tempanginsPhG_L_117.deg)
cor.test(graph_net_corr$T3_ysr_internalizing_sum, graph_net_corr$tempanginsPhG_L_117.deg)
tempanginsPhG_L_117.deg_cor <-
  graph_net_corr %>%
  ggplot(
    aes(
      x = tempanginsPhG_L_117.deg, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Temporal agranular insular PhG (R) - degree" 
  ) +
  labeltheme
tempanginsPhG_L_117.deg_cor

# degree of subgenual cingulate cortex (R) (sgCG_R_188.deg)
cor.test(graph_net_corr$T3_ysr_internalizing_sum, graph_net_corr$sgCG_R_188.deg)
sgCG_R_188.deg_cor <-
  graph_net_corr %>%
  ggplot(
    aes(
      x = sgCG_R_188.deg, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Subgenual Cingulate Cortex (R) - degree" 
  ) +
  labeltheme
sgCG_R_188.deg_cor

# deigenvector centrality of the rostral STG (R) (rostSTG_R_80.eig_cent)
cor.test(graph_net_corr$T3_ysr_internalizing_sum, graph_net_corr$rostSTG_R_80.eig_cent)
rostSTG_R_80.eig_cent_cor <-
  graph_net_corr %>%
  ggplot(
    aes(
      x = rostSTG_R_80.eig_cent, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Rostral STG (R) - eigenvector centrality" 
  ) +
  labeltheme
rostSTG_R_80.eig_cent_cor

# degree of the rostral STG (R) (rostSTG_R_79.deg)
cor.test(graph_net_corr$T3_ysr_internalizing_sum, graph_net_corr$rostSTG_L_79.deg)
rostSTG_L_79.deg_cor <-
  graph_net_corr %>%
  ggplot(
    aes(
      x = rostSTG_L_79.deg, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Rostral STG (L) - degree" 
  ) +
  labeltheme
rostSTG_L_79.deg_cor

# within module degree of the ventral ITG (R) (intvITG_R_90.wm_z)
cor.test(graph_net_corr$T3_ysr_internalizing_sum, graph_net_corr$intvITG_R_90.wm_z)
intvITG_R_90.wm_z_cor <-
  graph_net_corr %>%
  ggplot(
    aes(
      x = intvITG_R_90.wm_z, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Ventral ITG (R) - within module degree" 
  ) +
  labeltheme
intvITG_R_90.wm_z_cor

# participation coeff of the caudal mvOccC (rostcunMVocC_R_192.pc)
cor.test(graph_net_corr$T3_ysr_internalizing_sum, graph_net_corr$rostcunMVocC_R_192.pc)
rostcunMVocC_R_192.pc_cor <-
  graph_net_corr %>%
  ggplot(
    aes(
      x = rostcunMVocC_R_192.pc, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Caudal Medioventral Occipital Cortex - participation coefficient" 
  ) +
  labeltheme
rostcunMVocC_R_192.pc_cor

# within mod degree of the Occipital polar cortex (R) (ocpcLOcC_R_204.wm_z)
cor.test(graph_net_corr$T3_ysr_internalizing_sum, graph_net_corr$ocpcLOcC_R_204.wm_z)
ocpcLOcC_R_204.wm_z_cor <-
  graph_net_corr %>%
  ggplot(
    aes(
      x = ocpcLOcC_R_204.wm_z, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Occipital Polar Cortex (R) - within module degree" 
  ) +
  labeltheme
ocpcLOcC_R_204.wm_z_cor

brain_plus_all_ysr <-
  cowplot::plot_grid(
    si_cor, 
    externalizing_cor, 
    tempanginsPhG_L_117.deg_cor, 
    sgCG_R_188.deg_cor,
    rostSTG_R_80.eig_cent_cor, 
    intvITG_R_90.wm_z_cor, 
    rostcunMVocC_R_192.pc_cor, 
    ocpcLOcC_R_204.wm_z_cor,
    label_size = 10,
    ncol = 2
    )
ggsave("brain_+_all_ysr_cors.png", brain_plus_all_ysr, width = 7, height = 7)
```

-------------------------------------------------------------------------
# Only Psychological and Environmental factors 
T1_ysr_internalizing_sum, T1_ysr_externalizing_sum, T3_ysr_internalizing_sum, T3_ysr_externalizing_sum,  
Parent_Education.T1, BMI.T1, sumsev_type_t1, sss_t1, sex_child, Age_at_T3Bx, Age_at_T1 interval,  
tanner_average.T3, tanner_average.T1
glimpse(graph_net_stand_siq_brain)

```{r}
graph_net_select_onlyPsych <-
  graph_net_stand_siq_brain %>%
  dplyr::select(
    -ends_with(".eff_loc"), 
    -ends_with(".deg"), 
   -ends_with(".eig_cent"),
    -ends_with("pc"), 
    -ends_with(".wm_z"), 
    -meanFD,
    -meanGS,
    -sleepy,
   -fmap_applied
    )
```

```{r}
#as.matrix
predictors_ysr_scaled_nonbrain <- data.matrix(graph_net_select_onlyPsych[2:17]) # columns 2 - 17 are predictors
ysr_scaled_nonbrain <- graph_net_select_onlyPsych$T3_ysr_internalizing_sum_z # my response variable
save(predictors_ysr_scaled_nonbrain, file = "predictors_scaled_nonbrain_ysr.rda")
save(ysr_scaled_nonbrain, file = "ysr_scaled_nonbrain.rda")
```

## to get sense of coefficient path
```{r}
lasso_ysr_nonbrain <- glmnet(predictors_ysr_scaled_nonbrain, ysr_scaled_nonbrain, family = "gaussian", alpha = 1, standardize = FALSE)
# 
plot(lasso_ysr_nonbrain, xvar = "dev", label = TRUE)
```
# nested cv
```{r}
n <- 106

## Your procedure

cvfit <- cv.glmnet(predictors_ysr_scaled_nonbrain, ysr_scaled_nonbrain, standardize = FALSE, alpha = 1, nfolds = n)
betas <- coef(cvfit, s = "lambda.min")

# computing rsquared of unnested cv
# supp_siq_scaled is my y
X <- model.matrix(T3_ysr_internalizing_sum_z ~ ., data = graph_net_select_onlyPsych)[,-1]
# predict
y_hat <- predict(cvfit,  newx = X,  s = "lambda.min")
# R-Squared
r_sq <- 1 - (sum((ysr_scaled_nonbrain - y_hat)^2) / sum((ysr_scaled_nonbrain - mean(ysr_scaled_nonbrain))^2))
r_sq # 0.6080656 standardized prior to glmnet
cvfit$lambda.min # 0.04044414

## Get measure of performance of procedure
preds <- double(n)
ybars <- double(n)
for(i in 1:n){
    cvfit.inner <- cv.glmnet(predictors_ysr_scaled_nonbrain[-i,], ysr_scaled_nonbrain[-i], standardize = FALSE, nfolds = n-1, grouped=FALSE, alpha=1)
    preds[i] <- predict(cvfit.inner, newx = predictors_ysr_scaled_nonbrain[i,,drop=FALSE], s = "lambda.min")
    ybars[i] <- mean(ysr_scaled_nonbrain[-i])
    cat(i)
}

# total SS
mse0 <- mean((ysr_scaled_nonbrain-ybars)^2) # 1.009524
# mean square error
mse <- mean((ysr_scaled_nonbrain-preds)^2) # 0.4549446

R2 <-1- mse/mse0 # 0.5493473
```

# zero-order correlatoins

```{r}
graph_net_corr_onlypsych <- 
  graph_net_select_brain %>%
    dplyr::select(
    -ends_with(".eff_loc"), 
    -ends_with(".deg"), 
   -ends_with(".eig_cent"),
    -ends_with("pc"), 
    -ends_with(".wm_z"), 
    -meanFD,
    -meanGS,
    -sleepy,
   -fmap_applied,
   -siq_total.T3) %>%
  # converting race/ethinicity to factor and binarizing for analysis
  mutate(
    KSADS_Child_Race_by_P.T1 = factor(KSADS_Child_Race_by_P.T1),
    KSADS_Child_Race_by_P.T1_bin = ifelse(KSADS_Child_Race_by_P.T1 == "1", "1", "0"),
    # 1 = white, 0 = poc
    # converting sex and sleepiness to factor
    sex_child = factor(sex_child),
    sex_child = ifelse(sex_child == "2", "1", "0")
    ) %>%
  dplyr::select(-KSADS_Child_Race_by_P.T1) %>%
  dplyr::select(ELS_ID, T3_ysr_internalizing_sum, siq_total_log, everything())
graph_net_corr_onlypsych <-
  graph_net_corr_onlypsych %>%
  mutate_at(vars(KSADS_Child_Race_by_P.T1_bin, sex_child), factor) 
contrasts(graph_net_corr_onlypsych$KSADS_Child_Race_by_P.T1_bin) = contr.treatment(2)
contrasts(graph_net_corr_onlypsych$sex_child) = contr.treatment(2)
```

```{r}
labeltheme <- theme(axis.title.y = element_blank(),
                    text = element_text(size = 7))
# concurrent internalizing severity
cor.test(graph_net_corr_onlypsych$siq_total_log, graph_net_corr_onlypsych$T3_ysr_internalizing_sum)
si_t3_cor <-
  graph_net_corr_onlypsych %>%
  ggplot(
    aes(
      x = siq_total_log, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Concurrent Suicidal Ideation Severity"
  ) +
  labeltheme
si_t3_cor

# concurrent externalizing severity
cor.test(graph_net_corr_onlypsych$T3_ysr_internalizing_sum, graph_net_corr_onlypsych$T3_ysr_externalizing_sum)
extern_t3_cor <-
  graph_net_corr_onlypsych %>%
  ggplot(
    aes(
      x = T3_ysr_externalizing_sum, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Concurrent Externalizing Severity"
  ) +
  labeltheme
extern_t3_cor

# internalizing at baseline
cor.test(graph_net_corr_onlypsych$T3_ysr_internalizing_sum, graph_net_corr_onlypsych$T1_ysr_internalizing_sum)
intern_t1_cor <-
  graph_net_corr_onlypsych %>%
  ggplot(
    aes(
      x = T1_ysr_internalizing_sum, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Baseline Internalizing Severity"
  ) +
  labeltheme
intern_t1_cor

# sex
summary(lm(scale(T3_ysr_internalizing_sum) ~ sex_child, data = graph_net_corr_onlypsych))
sex_cor <-
  graph_net_corr_onlypsych %>%
  ggplot(
    aes(
      x = sex_child, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_boxplot() +
  theme_classic() +
  labs(
    x = "Sex"
    ) +
  labeltheme
sex_cor


# interval
cor.test(graph_net_corr_onlypsych$T3_ysr_internalizing_sum, graph_net_corr_onlypsych$interval)
interval_cor <-
  graph_net_corr_onlypsych %>%
  ggplot(
    aes(
      x = interval, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Interval between baseline and follow-up"
  ) +
  labeltheme
interval_cor

# tanner  at follow up
cor.test(graph_net_corr_onlypsych$T3_ysr_internalizing_sum, graph_net_corr_onlypsych$tanner_average.T3)
tannert3_cor <-
  graph_net_corr_onlypsych %>%
  ggplot(
    aes(
      x = tanner_average.T3, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Concurrent Tanner Stage"
  ) +
  labeltheme
tannert3_cor

# race  
summary(lm(scale(T3_ysr_internalizing_sum) ~ KSADS_Child_Race_by_P.T1_bin, data = graph_net_corr_onlypsych))
race_cor <-
  graph_net_corr_onlypsych %>%
  ggplot(
    aes(
      x = KSADS_Child_Race_by_P.T1_bin, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_boxplot() +
  theme_classic() +
  labs(
    x = "Race/Ethnicity"
  ) +
  labeltheme
race_cor

# age  
cor.test(graph_net_corr_onlypsych$T3_ysr_internalizing_sum, graph_net_corr_onlypsych$Age_at_T1)
Age_at_T1_cor <-
  graph_net_corr_onlypsych %>%
  ggplot(
    aes(
      x = Age_at_T1, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Age at baseline"
  ) +
  labeltheme
Age_at_T1_cor



nonbrain_ysr <-
  cowplot::plot_grid(
    si_t3_cor,
    extern_t3_cor,
    intern_t1_cor,
    tannert3_cor,
    sex_cor,
    interval_cor,
    race_cor,
    Age_at_T1_cor,
    label_size = 10,
    ncol = 3
    )
ggsave("nonbrain_cors_ysr.png", nonbrain_ysr)
```


-------------------------------------------------------------------------


# Only Brain and brain related factors (global signal, meanfd, sleepiness)

## de-selecting variables
```{r}
graph_net_stand_siq_onlybrain <- graph_net_stand_siq_brain %>%
  dplyr::select(
    T3_ysr_internalizing_sum_z,
    ends_with(".eff_loc"), 
    ends_with(".deg"), 
    ends_with(".eig_cent"),
    ends_with("pc"), 
    ends_with(".wm_z"), 
    meanFD,
    meanGS,
    sleepy,
    fmap_applied
    ) %>%
  mutate(
    sleepy = factor(sleepy),
    fmap_applied = factor(fmap_applied)
  )
```


#### constructing x matrix and y vector
```{r}
#as.matrix
predictors_scaled_ysr_onlybrain <- data.matrix(graph_net_stand_siq_onlybrain[2:1255]) # columns 2 - 1255 are predictors
response_ysr <-graph_net_stand_siq_onlybrain$T3_ysr_internalizing_sum_z # my response variable
save(predictors_scaled_ysr_onlybrain, file = "predictors_scaled_ysr_onlybrain.rda")
save(response_ysr, file = "response_ysr.rda")
```

## to get sense of coefficient path
```{r}
lasso_onlybrain <- glmnet(predictors_scaled_ysr_onlybrain, response_ysr, family = "gaussian", alpha = 1, standardize = FALSE)
# 
plot(lasso_onlybrain, xvar = "dev", label = TRUE)
```

```{r}
n <- 106

## Your procedure

cvfit <- cv.glmnet(predictors_scaled_ysr_onlybrain, response_ysr, standardize = FALSE, alpha = 1, nfolds = n)
betas <- coef(cvfit, s = "lambda.min")
# computing rsquared of unnested cv
# supp_siq_scaled is my y
X <- model.matrix(T3_ysr_internalizing_sum_z ~ ., data = graph_net_stand_siq_onlybrain)[,-1]
# predict
y_hat <- predict(cvfit,  newx = X,  s = "lambda.min")
# R-Squared
r_sq <- 1 - (sum((response_ysr - y_hat)^2) / sum((response_ysr - mean(response_ysr))^2))
r_sq # 0.4295407 standardized prior to glmnet
cvfit$lambda.min # 0.1617792


## Get measure of performance of procedure
preds <- double(n)
ybars <- double(n)
for(i in 1:n){
    cvfit.inner <- cv.glmnet(predictors_scaled_ysr_onlybrain[-i,], response_ysr[-i], standardize = FALSE, nfolds = n-1, grouped=FALSE, alpha=1)
    preds[i] <- predict(cvfit.inner, newx = predictors_scaled_ysr_onlybrain[i,,drop=FALSE], s = "lambda.min")
    ybars[i] <- mean(response_ysr[-i])
    cat(i)
}

mse0 <- mean((response_ysr-ybars)^2) # 1.009524
mse <- mean((response_ysr-preds)^2) # 1.140252

R2 <-1- mse/mse0 #-0.1294951
```

# zero order correlations
```{r}
graph_net_corr_onlybrain <- 
  graph_net_select_brain %>%
  # converting race/ethinicity to factor and binarizing for analysis
  dplyr::select(
    ELS_ID,
    T3_ysr_internalizing_sum,
    ends_with(".eff_loc"), 
    ends_with(".deg"), 
    ends_with(".eig_cent"),
    ends_with("pc"), 
    ends_with(".wm_z"), 
    meanFD,
    meanGS,
    sleepy,
    fmap_applied
    ) %>%
  mutate(
    sleepy = factor(sleepy),
    fmap_applied = factor(fmap_applied)
    ) %>%
  dplyr::select(ELS_ID, T3_ysr_internalizing_sum, everything())
graph_net_corr_onlybrain <-
  graph_net_corr_onlybrain %>%
  mutate_at(vars(sleepy, fmap_applied), factor)
contrasts(graph_net_corr_onlybrain$sleepy) = contr.treatment(2)
contrasts(graph_net_corr_onlybrain$fmap_applied) = contr.treatment(2)
```

```{r}
labeltheme <- theme(axis.title.y = element_blank(),
                    text = element_text(size = 7))
# within mod degree of theIntermediate ventral inferior temporal gyrus (R) (intvITG_R_90.wm_z)
cor.test(graph_net_corr_onlybrain$T3_ysr_internalizing_sum, graph_net_corr_onlybrain$intvITG_R_90.wm_z)
intvITG_R_90.wm_z_cor <-
  graph_net_corr_onlybrain %>%
  ggplot(
    aes(
      x = intvITG_R_90.wm_z, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Ventral ITG (R) - within-module degree"
  ) + 
  labeltheme
intvITG_R_90.wm_z_cor

# eig cent of the  rostral STG (R) (rostSTG_R_80.eig_cent)
cor.test(graph_net_corr_onlybrain$T3_ysr_internalizing_sum, graph_net_corr_onlybrain$rostSTG_R_80.eig_cent)
rostSTG_R_80.eig_cent_cor <-
  graph_net_corr_onlybrain %>%
  ggplot(
    aes(
      x = rostSTG_R_80.eig_cent, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "rostral STG (R) - eigenvector centrality"
  ) + 
  labeltheme
rostSTG_R_80.eig_cent_cor 

#participation coeff of the intermediate ventral inferior temporal gyrus (vlITG_R_98.pc )
cor.test(graph_net_corr_onlybrain$T3_ysr_internalizing_sum, graph_net_corr_onlybrain$vlITG_R_98.pc)
vlITG_R_98.pc_cor <-
  graph_net_corr_onlybrain %>%
  ggplot(
    aes(
      x = vlITG_R_98.pc, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Ventral ITG (R) - participation coefficient"
  ) + 
  labeltheme 
vlITG_R_98.pc_cor

# within module degree of the occipital polar cortex (R) (ocpcLOcC_R_204.wm_z)
cor.test(graph_net_corr_onlybrain$T3_ysr_internalizing_sum, graph_net_corr_onlybrain$ocpcLOcC_R_204.wm_z)
ocpcLOcC_R_204.wm_z_cor <-
  graph_net_corr_onlybrain %>%
  ggplot(
    aes(
      x = ocpcLOcC_R_204.wm_z, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Occipital Polar Cortex (R) - within module degree"
  ) + 
  labeltheme 
ocpcLOcC_R_204.wm_z_cor

# degree of the sgACC (R) (sgCG_R_188.deg )
cor.test(graph_net_corr_onlybrain$T3_ysr_internalizing_sum, graph_net_corr_onlybrain$sgCG_R_188.deg)
sgCG_R_188.deg_cor <-
  graph_net_corr_onlybrain %>%
  ggplot(
    aes(
      x = sgCG_R_188.deg, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Subgenual Cingulate Cortex (R) - degree"
  ) + 
  labeltheme
sgCG_R_188.deg_cor


# local efficiency of the substantia nigra (L) (SN_L_225.eff_loc)
cor.test(graph_net_corr_onlybrain$T3_ysr_internalizing_sum, graph_net_corr_onlybrain$SN_L_225.eff_loc)
SN_L_225.eff_loc_cor <-
  graph_net_corr_onlybrain %>%
  ggplot(
    aes(
      x = SN_L_225.eff_loc, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Substantia Nigra (L) - local efficiency"
  ) + 
  labeltheme
SN_L_225.eff_loc_cor

# Participation coeff of the medial precuneus (medPcun_L_149.pc )
cor.test(graph_net_corr_onlybrain$T3_ysr_internalizing_sum, graph_net_corr_onlybrain$medPcun_L_149.pc)
medPcun_L_149.pc_cor <-
  graph_net_corr_onlybrain %>%
  ggplot(
    aes(
      x = medPcun_L_149.pc, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Medial Precuneus (L) - participation coefficient"
  ) + 
  labeltheme 
medPcun_L_149.pc_cor

# local efficiency of the right medial OrG (medSTG_R_70.eff_loc)
cor.test(graph_net_corr_onlybrain$T3_ysr_internalizing_sum, graph_net_corr_onlybrain$medSTG_R_70.eff_loc)
medSTG_R_70.eff_loc_cor <-
  graph_net_corr_onlybrain %>%
  ggplot(
    aes(
      x = medSTG_R_70.eff_loc, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Medial STG (R) - local efficiency"
  ) + 
  labeltheme 
medSTG_R_70.eff_loc_cor

# participation coeff of the medial PhG (medPhG_L_119.pc)
cor.test(graph_net_corr_onlybrain$T3_ysr_internalizing_sum, graph_net_corr_onlybrain$medPhG_L_119.pc)
medPhG_L_119.pc_cor <-
  graph_net_corr_onlybrain %>%
  ggplot(
    aes(
      x = medPhG_L_119.pc, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Medial PhG (R) - participation coefficient"
  ) + 
  labeltheme 
medPhG_L_119.pc_cor


# degree of the Temporal agranular insular parahippocampal gyrus (L) (tempanginsPhG_L_117.deg)
cor.test(graph_net_corr_onlybrain$T3_ysr_internalizing_sum, graph_net_corr_onlybrain$tempanginsPhG_L_117.deg)
tempanginsPhG_L_117.deg_cor <-
  graph_net_corr_onlybrain %>%
  ggplot(
    aes(
      x = tempanginsPhG_L_117.deg, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Temporal agranular insular parahippocampal gyrus (L) - degree"
  ) + 
  labeltheme
tempanginsPhG_L_117.deg_cor

# local efficiency of the  occipital polar cortex (R) (ocpcLOcC_R_204.eff_loc)
cor.test(graph_net_corr_onlybrain$T3_ysr_internalizing_sum, graph_net_corr_onlybrain$ocpcLOcC_R_204.eff_loc)
ocpcLOcC_R_204.eff_loc_cor <-
  graph_net_corr_onlybrain %>%
  ggplot(
    aes(
      x = ocpcLOcC_R_204.eff_loc, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Occipital Polar Cortex (R) - local efficiency"
  ) + 
  labeltheme
ocpcLOcC_R_204.eff_loc_cor 

# Within mod degree of the temporal agranular insular PhG (R) (tempanginsPhG_R_118.wm_z)
cor.test(graph_net_corr_onlybrain$T3_ysr_internalizing_sum, graph_net_corr_onlybrain$tempanginsPhG_R_118.wm_z)
tempanginsPhG_R_118.wm_z_cor <-
  graph_net_corr_onlybrain %>%
  ggplot(
    aes(
      x = tempanginsPhG_R_118.wm_z, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Temporal agranular insular PhG (R) - within module degree"
  ) + 
  labeltheme 
tempanginsPhG_R_118.wm_z_cor

# degree of the rostral superior temporal gyrus (L) (rostSTG_L_79.deg)
cor.test(graph_net_corr_onlybrain$T3_ysr_internalizing_sum, graph_net_corr_onlybrain$rostSTG_L_79.deg)
rostSTG_L_79.deg_cor <-
  graph_net_corr_onlybrain %>%
  ggplot(
    aes(
      x = rostSTG_L_79.deg, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Rostral STG (L) - degree"
  ) + 
  labeltheme 
rostSTG_L_79.deg_cor

# within mod degree of the  medial superior frontal gyrus (R) (medSFG_R_14.wm_z)
cor.test(graph_net_corr_onlybrain$T3_ysr_internalizing_sum, graph_net_corr_onlybrain$medSFG_R_14.wm_z)
medSFG_R_14.wm_z_cor <-
  graph_net_corr_onlybrain %>%
  ggplot(
    aes(
      x = medSFG_R_14.wm_z, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Medial SFG (R) - within-module degree"
  ) + 
  labeltheme
medSFG_R_14.wm_z_cor 

# degree of the temporal agranular insular PhG (L) (tempanginsPhG_L_117.wm_z)
cor.test(graph_net_corr_onlybrain$T3_ysr_internalizing_sum, graph_net_corr_onlybrain$tempanginsPhG_L_117.wm_z)
tempanginsPhG_L_117.wm_z_cor <-
  graph_net_corr_onlybrain %>%
  ggplot(
    aes(
      x = tempanginsPhG_L_117.wm_z, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Temporal agranular insular PhG (L) - within module degree"
  ) + 
  labeltheme 
tempanginsPhG_L_117.wm_z_cor

# local efficiency of theleft medial OrG (medOrG_R_48.eig_cent)
cor.test(graph_net_corr_onlybrain$T3_ysr_internalizing_sum, graph_net_corr_onlybrain$medOrG_R_48.eig_cent)
medOrG_R_48.eig_cent_cor <-
  graph_net_corr_onlybrain %>%
  ggplot(
    aes(
      x = medOrG_R_48.eig_cent, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Medial orbital frontal gyrus (R) - eigenvector centrality"
  ) + 
  labeltheme 
medOrG_R_48.eig_cent_cor

# eigenvector centrality of the right lateral middle occiptial gyrus (mocgLOcC_R_200.eff_loc)
cor.test(graph_net_corr_onlybrain$T3_ysr_internalizing_sum, graph_net_corr_onlybrain$mocgLOcC_R_200.eff_loc)
mocgLOcC_R_200.eff_loc_cor <-
  graph_net_corr_onlybrain %>%
  ggplot(
    aes(
      x = mocgLOcC_R_200.eff_loc, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Lateral Middle Occiptial Gyrus (R) - local efficiency"
  ) + 
  labeltheme 
mocgLOcC_R_200.eff_loc_cor

# within mod degree of the lateral ventral FuG (R) (latventFuG_R_108.wm_z )
cor.test(graph_net_corr_onlybrain$T3_ysr_internalizing_sum, graph_net_corr_onlybrain$latventFuG_R_108.wm_z)
latventFuG_R_108.wm_z_cor <-
  graph_net_corr_onlybrain %>%
  ggplot(
    aes(
      x = latventFuG_R_108.wm_z, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Lateral ventral FuG (R) - within module degree"
  ) + 
  labeltheme
latventFuG_R_108.wm_z_cor 


# degree of the right substantia nigra (R)
cor.test(graph_net_corr_onlybrain$T3_ysr_internalizing_sum, graph_net_corr_onlybrain$SN_R_226.deg)
SN_R_226.deg_cor <-
  graph_net_corr_onlybrain %>%
  ggplot(
    aes(
      x = SN_R_226.deg , 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Substantia Nigra (R) - degree"
  ) + 
  labeltheme 
SN_R_226.deg_cor

# degree of the Rostroventral inferior parietal lobe (R) (rostventIPL_R_144.deg)
cor.test(graph_net_corr_onlybrain$T3_ysr_internalizing_sum, graph_net_corr_onlybrain$rostventIPL_R_144.deg)
rostventIPL_R_144.deg_cor <-
  graph_net_corr_onlybrain %>%
  ggplot(
    aes(
      x = rostventIPL_R_144.deg, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Rostroventral inferior parietal lobe (R)  - degree"
  ) + 
  labeltheme 
rostventIPL_R_144.deg_cor


# participation coeff of the Medio ventral rostral lingual gyrus (L) (rostlingMVocC_L_195.pc)
cor.test(graph_net_corr_onlybrain$T3_ysr_internalizing_sum, graph_net_corr_onlybrain$rostlingMVocC_L_195.pc)
rostlingMVocC_L_195.pc_cor <-
  graph_net_corr_onlybrain %>%
  ggplot(
    aes(
      x = rostlingMVocC_L_195.pc, 
      y = T3_ysr_internalizing_sum
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Medio ventral rostral lingual gyrus (L) - participation coefficient"
  ) + 
  labeltheme 
rostlingMVocC_L_195.pc_cor

# participation coeff of the Rostral superior parietal lobe (R) (rostSPL_R_126.pc)
cor.test(graph_net_corr_onlybrain$T3_ysr_internalizing_sum, graph_net_corr_onlybrain$rostSPL_R_126.pc)
rostSPL_R_126.pc_cor <-
  graph_net_stand_siq_brain %>%
  ggplot(
    aes(
      x = rostSPL_R_126.pc, 
      y = T3_ysr_internalizing_sum_z
      )
    ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic() +
  labs(
    x = "Rostral superior parietal lobe (R) - participation coefficient"
  ) + 
  labeltheme 
rostSPL_R_126.pc_cor

brain <-
  cowplot::plot_grid(
    intvITG_R_90.wm_z_cor,    
    rostSTG_R_80.eig_cent_cor, 
    vlITG_R_98.pc_cor,
    ocpcLOcC_R_204.eff_loc_cor,
    sgCG_R_188.deg_cor,
    SN_L_225.eff_loc_cor,
    medPcun_L_149.pc_cor,
    medSTG_R_70.eff_loc_cor,   
    medPhG_L_119.pc_cor,    
    tempanginsPhG_L_117.deg_cor,
    ocpcLOcC_R_204.wm_z_cor,
    tempanginsPhG_R_118.wm_z_cor,
    rostSTG_L_79.deg_cor,
    medSFG_R_14.wm_z_cor,    
    tempanginsPhG_L_117.wm_z_cor,    
    medOrG_R_48.eig_cent_cor,
    mocgLOcC_R_200.eff_loc_cor,
    latventFuG_R_108.wm_z_cor,
    SN_R_226.deg_cor,
    rostventIPL_R_144.deg_cor,
    rostlingMVocC_L_195.pc_cor,
    rostSPL_R_126.pc_cor,
    label_size = 10,
    ncol = 3
    )
ggsave("brain_cors_ysr.png", brain, width = 7, height = 10)
```

