---
title: "10_snl_to_bg"
author: "Jackie"
date: "6/9/2020"
output: html_notebook
---

```{r}

library(tidyverse)
library(modelr)
library(R.matlab)
library(purrr)
library(repurrrsive)
library(magrittr)
library(readxl)

```

# read in els id
```{r}
var_subjs = "~/Box/var_subjs.csv"
ELS_ID <- read_csv(var_subjs) %>%
  dplyr::select(Subj_ID, ELS_ID)
```


# load files
```{r}
file_subj_name <- list.files(
  path = "~/Box/CorrelationMatrices_Fish",
  pattern = "*.mat", full.names = FALSE 
)
files <- list.files(
  path = "~/Box/CorrelationMatrices_Fish",
  pattern = "*.mat", full.names = TRUE)

file_comb <- cbind(files, file_subj_name)
```

# combine mat files  and extract corr matrices from each
```{r}
# combining mat files into a list
tbl <- rbind(lapply(file_comb[,1],
  readMat)
  )
tbl_corr <- map(tbl, extract, c("fish.corr")) 
```

# load nodes
```{r}
nodes_fp <- "~/Box/BrainRegions.xlsx"

nodes <- read_excel(nodes_fp, col_names = FALSE)
```

# Renaming variables for nodes file
```{r}
nodes <-
  nodes %>%
  rename(
    "include" = `...1`,
    "brainnetome_name" = `...2`,
    "brain_name" = `...3`,
    "x" = `...4`,
    "y" = `...5`,
    "z" = `...6`
  ) %>%
  mutate(
    brainnetome_name = as.factor(brainnetome_name),
    brain_name = as.factor(brain_name)
  )
```

## exttracting brain_name
```{r}
#
names <- c("SFG_L_1", "SFG_R_2", "SFG_L_3", "SFG_R_4", "SFG_L_5", "SFG_R_6", "SFG_L_7",  "SFG_R_8", "SFG_L_9", "SFG_R_10", "SFG_L_11", "SFG_R_12", "SFG_L_13", "SFG_R_14", "MFG_L_15", "MFG_R_16", "MFG_L_17", "MFG_R_18", "MFG_L_19", "MFG_R_20", "MFG_L_21", "MFG_R_22", "MFG_L_23", "MFG_R_24", "MFG_L_25", "MFG_R_26", "MFG_L_27", "MFG_R_28", "IFG_L_29", "IFG_R_30", "IFG_L_31", "IFG_R_32", "IFG_L_33", "IFG_R_34", "IFG_L_35", "IFG_R_36", "IFG_L_37", "IFG_R_38", "IFG_L_39", "IFG_R_40", "OrG_L_41", "OrG_R_42", "OrG_L_43", "OrG_R_44", "OrG_L_45", "OrG_R_46", "OrG_L_47", "OrG_R_48", "OrG_L_49", "OrG_R_50", "OrG_L_51", "OrG_R_52", "PrG_L_53", "PrG_R_54", "PrG_L_55", "PrG_R_56", "PrG_L_57", "PrG_R_58", "PrG_L_59", "PrG_R_60", "PrG_L_61", "PrG_R_62", "PrG_L_63", "PrG_R_64", "PCL_L_65", "PCL_R_66", "PCL_L_67", "PCL_R_68", "STG_L_69", "STG_R_70", "STG_L_71", "STG_R_72", "STG_L_73", "STG_R_74", "STG_L_75", "STG_R_76", "STG_L_77", "STG_R_78", "STG_L_79", "STG_R_80", "MTG_L_81", "MTG_R_82", "MTG_L_83", "MTG_R_84", "MTG_L_85", "MTG_R_86", "MTG_L_87", "MTG_R_88", "ITG_L_89", "ITG_R_90", "ITG_L_91", "ITG_R_92", "ITG_L_93", "ITG_R_94", "ITG_L_95", "ITG_R_96", "ITG_L_97", "ITG_R_98", "ITG_L_99", "ITG_R_100", "ITG_L_101", "ITG_R_102", "FuG_L_103", "FuG_R_104", "FuG_L_105", "FuG_R_106", "FuG_L_107", "FuG_R_108", "PhG_L_109", "PhG_R_110", "PhG_L_111", "PhG_R_112", "PhG_L_113", "PhG_R_114", "PhG_L_115", "PhG_R_116", "PhG_L_117", "PhG_R_118", "PhG_L_119", "PhG_R_120", "pSTS_L_121", "pSTS_R_122", "pSTS_L_123", "pSTS_R_124", "SPL_L_125", "SPL_R_126", "SPL_L_127", "SPL_R_128", "SPL_L_129", "SPL_R_130", "SPL_L_131", "SPL_R_132", "SPL_L_133", "SPL_R_134", "IPL_L_135", "IPL_R_136", "IPL_L_137", "IPL_R_138", "IPL_L_139", "IPL_R_140", "IPL_L_141", "IPL_R_142", "IPL_L_143", "IPL_R_144", "IPL_L_145", "IPL_R_146", "Pcun_L_147", "Pcun_R_148", "Pcun_L_149", "Pcun_R_150", "Pcun_L_151", "Pcun_R_152", "Pcun_L_153", "Pcun_R_154", "PoG_L_155", "PoG_R_156", "PoG_L_157", "PoG_R_158", "PoG_L_159", "PoG_R_160", "PoG_L_161", "PoG_R_162", "INS_L_163", "INS_R_164", "INS_L_165", "INS_R_166", "INS_L_167", "INS_R_168", "INS_L_169", "INS_R_170", "INS_L_171", "INS_R_172", "INS_L_173", "INS_R_174", "CG_L_175", "CG_R_176", "CG_L_177", "CG_R_178", "CG_L_179", "CG_R_180", "CG_L_181", "CG_R_182", "CG_L_183", "CG_R_184", "CG_L_185", "CG_R_186", "CG_L_187", "CG_R_188", "MVocC_L_189", "MVocC_R_190", "MVocC_L_191", "MVocC_R_192", "MVocC_L_193", "MVocC_R_194", "MVocC_L_195", "MVocC_R_196", "MVocC_L_197", "MVocC_R_198", "LOcC_L_199", "LOcC_R_200", "LOcC_L_201", "LOcC_R_202", "LOcC_L_203", "LOcC_R_204", "LOcC_L_205", "LOcC_R_206", "LOcC_L_207", "LOcC_R_208", "LOcC_L_209", "LOcC_R_210", "Amyg_L_211", "Amyg_R_212", "Amyg_L_213", "Amyg_R_214", "Hipp_L_215", "Hipp_R_216", "Hipp_L_217", "Hipp_R_218", "vCA_L_219", "vCA_R_220", "Gpe_L_221", "Gpe_R_222", "Gpi_L_223", "Gpi_R_224", "SN_L_225", "SN_R_226", "NAC_L_229", "NAC_R_230", "vmPu_L_231", "vmPU_R_232", "dCa_L_233", "dCA_R_234", "dlPu_L_235", "dlPu_R_236", "mPFtha_L_237", "mPFtha_R_238", "mPMtha_L_239", "mPMtha_R_240", "Stha_L_241", "Stha_R_242", "rTtha_L_243", "rTtha_R_244", "Pptha_L_245", "Ppptha_R_246", "Otha_L_247", "Otha_R_248", "cTtha_L_249", "cTtha_R_250", "lPFtha_L_251", "lPFtha_R_252")
rois <- data.frame(names) %>%
  rename(rois = names)

```

```{r}
bg <- c("vCA_L_219", "vCA_R_220", "Gpe_L_221", "Gpe_R_222", "Gpi_L_223", "Gpi_R_224", "SN_L_225", "SN_R_226", "NAC_L_229", "NAC_R_230", "vmPu_L_231", "vmPU_R_232", "dCa_L_233", "dCA_R_234", "dlPu_L_235", "dlPu_R_236")
```


### just a test
```{r}
z = as.matrix(tbl_corr[[55]][["fish.corr"]])
colnames(z) <- names
z <- cbind(rois, z)
zz <- z %>%
  dplyr:: select(rois, vCA_L_219:dlPu_R_236) %>%
  mutate(bgs = rois %in% bg) %>%
  filter(bgs == TRUE) %>%
  dplyr::select(-bgs) %>%
  filter(rois == "SN_R_226")

zz[zz<0] <- 0

zz_ind <-
  zz %>%
  rename_at(
    vars(-rois),
    function(x)
      paste0(x, "-SN_R_226")
    ) 
```

## for everyone
```{r}

tbl_corr_mats <- NULL
subj <- NULL
subjs <- NULL


for (i in seq_along(tbl_corr)) {
  
  subj = as.matrix(tbl_corr[[i]][["fish.corr"]])
  
  colnames(subj) <- names
  subj <- cbind(rois, subj)
  
  subjs <- subj %>%
  dplyr:: select(rois, vCA_L_219:dlPu_R_236) %>%
  mutate(bgs = rois %in% bg) %>%
  filter(bgs == TRUE) %>%
  dplyr::select(-bgs) %>%
  filter(rois == "SN_R_226") %>%
  rename_at(
    vars(-rois),
    function(x)
      paste0(x, ".SN_R_226")
    )
  
  tbl_corr_mats = rbind(tbl_corr_mats, subjs)

}

```



```{r}
# converting corr_means matrix to dataframe and renaming variable
tbl_corr_mats_df <-
  tbl_corr_mats %>%
  data.frame() %>%
  rownames_to_column(var = "id")

tbl_corr_mats_comb <- cbind(ELS_ID, tbl_corr_mats_df)

# setting neg weights to zero
tbl_corr_mats_comb[, 5:20][tbl_corr_mats_comb[, 5:20] < 0] <- 0
```

# read in suicide data
```{r}

siq_fp <- "~/Box/siq_graph.csv"

siq <- read_csv(siq_fp) %>%
  dplyr::select(ELS_ID, siq_total_log)
```

```{r}
options(scipen=999) 
z_score <- function(x) {
diff_mu <- x - mean(x, na.rm = T)
sd <- sd(x, na.rm = T)
diff_mu / sd
}
```

```{r}
stand_siq <- siq %>%
  mutate(siq_total_log_z = scale(siq_total_log, center = TRUE, scale = TRUE),
         ELS_ID = factor(ELS_ID))

bg_corrs <- tbl_corr_mats_comb %>%
  mutate(ELS_ID = factor(ELS_ID))

# merging
bg_corr_and_siq <- left_join(stand_siq, bg_corrs, by = "ELS_ID")

# deselecting variables
bg_corr_and_siq <- bg_corr_and_siq %>%
  dplyr::select(-Subj_ID, -id, -rois, -siq_total_log, -SN_R_226.SN_R_226)

# standardizing predictors
bg_corr_and_siq_stand <- bg_corr_and_siq %>%
  mutate_at(vars(-ELS_ID, -siq_total_log_z), z_score)

bg_corr_and_siq_fp <- "~/Box/bg_corr_and_siq.csv"
write_csv(bg_corr_and_siq, bg_corr_and_siq_fp)

bg_corr_and_siq_stand_fp <- "~/Box/bg_corr_and_siq_stand.csv"
write_csv(bg_corr_and_siq_stand, bg_corr_and_siq_stand_fp)
```

```{r}
library(corrplot)
library(corrr)
corr <- 
  bg_corr_and_siq_stand %>%
  dplyr::select(
    ends_with("SN_R_226")
    ) %>%
  cor()

cor_tbl <- 
  bg_corr_and_siq_stand %>%
  dplyr::select(
    ends_with("SN_R_226")
  ) %>% 
  correlate(use = "complete.obs", method = "spearman") %>% 
  fashion()
cor_tbl

png(height=800, width=800, file="bg_corr_siq")
corrplot(corr, 
         method = "color",
         order = "hclust",
         tl.cex = 1, 
         tl.col = "black", 
         type = "upper")
dev.off()
```

The atlas includes six subcorticalnuclei:thestriatum(STR),the globus pallidus internal and external segment(GPi/e),the subthalamic nucleus(STN),the
substantia nigra(SN),and the rednucleus(RN).

We have 16 s2s variables. Need to penalize. PErforming best subset

Select the subset of predictors that do the best at meeting some well-defined objective criterion, such as having the largest R2 value or the smallest MSE, Mallow’s Cp or AIC

From: https://olsrr.rsquaredacademy.com/articles/variable_selection.html#best-subset-regression

```{r}
# library(devtools)
# install_github(repo="ryantibs/best-subset", subdir="bestsubset")
library(olsrr)

test <- lm(siq_total_log_z ~ vCA_L_219.SN_R_226 + vCA_R_220.SN_R_226 + Gpe_L_221.SN_R_226 + Gpe_R_222.SN_R_226 +Gpi_L_223.SN_R_226 + Gpi_R_224.SN_R_226 +SN_L_225.SN_R_226 + NAC_L_229.SN_R_226 + NAC_R_230.SN_R_226 +  vmPu_L_231.SN_R_226 + vmPU_R_232.SN_R_226 + dCa_L_233.SN_R_226 + dCA_R_234.SN_R_226 + dlPu_L_235.SN_R_226 + dlPu_R_236.SN_R_226,data = bg_corr_and_siq_stand)

k <- ols_step_best_subset(test)
k
plot(k)

# model 4 seems to be the best
#4         Gpe_L_221.SN_R_226 SN_L_225.SN_R_226 vmPu_L_231.SN_R_226 vmPU_R_232.SN_R_226
# # 4        0.1079      0.0707     -0.0059    -0.0690    286.0868     0.5440    301.7775    93.8849    0.9753    0.0098    0.9850 
k$adjr
```


## trying with the leaps package
From: https://rpubs.com/davoodastaraky/subset

```{r}
library(leaps)
fit_all = regsubsets(siq_total_log_z ~ vCA_L_219.SN_R_226 + vCA_R_220.SN_R_226 + Gpe_L_221.SN_R_226 + Gpe_R_222.SN_R_226 +Gpi_L_223.SN_R_226 + Gpi_R_224.SN_R_226 +SN_L_225.SN_R_226 + NAC_L_229.SN_R_226 + NAC_R_230.SN_R_226 +  vmPu_L_231.SN_R_226 + vmPU_R_232.SN_R_226 + dCa_L_233.SN_R_226 + dCA_R_234.SN_R_226 + dlPu_L_235.SN_R_226 + dlPu_R_236.SN_R_226, data = bg_corr_and_siq_stand)
summary(fit_all)
modelfit <- summary(fit_all)
names(modelfit) 
r_sq <- modelfit$rsq
cp <- modelfit$cp
```
Plotting RSS, adjusted R2, Cp, and BIC 

From: https://rpubs.com/davoodastaraky/subset

```{r}

plot(modelfit$rss ,xlab="Number of Variables ",ylab="RSS",type="l")
which.min(modelfit$rss)
plot(modelfit$adjr2 ,xlab="Number of Variables ", ylab="Adjusted RSq",type="l")
which.max(modelfit$adjr2)
plot(modelfit$cp ,xlab="Number of Variables ",ylab="Cp", type='l')
which.min(modelfit$cp )
plot(modelfit$bic ,xlab="Number of Variables ",ylab="BIC",type='l')
which.min(modelfit$bic )
```


```{r}
estimates <- coef(fit_all ,4)
estimates <- as.data.frame(estimates) %>%
  rownames_to_column()
bg_corr_si_estimates_fp <- "~/Box/bg_corr_si_estimates.csv"
write_csv(estimates, bg_corr_si_estimates_fp)
```

