---
title: "graph_t1_degree"
author: "Jackie"
date: "4/21//2021"
output: html_notebook
---

Computes AUC for degree (not normalized)

# libraries
```{r message=FALSE}
library(tidyverse)
library(haven)
library(modelr)
library(readxl)
library(Rcpp)
library(httpuv)
library(shiny)
library(plotly)
```

# reading data
```{r message=FALSE}
deg_fp <- "~/Box/Mooddata_Coordinating/1_Lab_Coordinating/Users/JackieSchwartz/PHIND_RS_and_Suicide/April2021Analysis/deg.xlsx"
deg_th.1 <-
  read_excel(deg_fp, sheet = "deg_.1")
deg_th.12 <-
  read_excel(deg_fp, sheet = "deg_.12")
deg_th.14 <-
  read_excel(deg_fp, sheet = "deg_.14")
deg_th.16 <-
  read_excel(deg_fp, sheet = "deg_.16")
deg_th.18 <-
  read_excel(deg_fp, sheet = "deg_.18")
deg_th.2 <-
  read_excel(deg_fp, sheet = "deg_.2")
```

# Renaming
```{r}
deg_th.1 <-
  deg_th.1 %>%
  rename(
    "ELS_ID" = "...1"
  )
deg_th.12 <-
  deg_th.12 %>%
  rename(
    "ELS_ID" = "...1"
  )
deg_th.14 <-
  deg_th.14 %>%
  rename(
    "ELS_ID" = "...1"
  )
deg_th.16 <-
  deg_th.16 %>%
  rename(
    "ELS_ID" = "...1"
  )
deg_th.18 <-
  deg_th.18 %>%
  rename(
    "ELS_ID" = "...1"
  )
deg_th.2 <-
  deg_th.2 %>%
  rename(
    "ELS_ID" = "...1"
  )
```


# Renaming subject column 
```{r}

deg_th.1 <-
  deg_th.1 %>%
  mutate(ELS_ID = 
    str_remove(ELS_ID,
               "sub-")
  ) %>%
  mutate(ELS_ID = as.numeric(ELS_ID))
deg_th.12 <-
  deg_th.12  %>%
  mutate(ELS_ID = 
    str_remove(ELS_ID,
               "sub-")
  ) %>%
  mutate(ELS_ID = as.numeric(ELS_ID))
deg_th.14 <-
  deg_th.14  %>%
  mutate(ELS_ID = 
    str_remove(ELS_ID,
               "sub-")
  ) %>%
  mutate(ELS_ID = as.numeric(ELS_ID))
deg_th.16 <-
  deg_th.16  %>%
  mutate(ELS_ID = 
    str_remove(ELS_ID,
               "sub-")
  ) %>%
  mutate(ELS_ID = as.numeric(ELS_ID))
deg_th.18 <-
  deg_th.18  %>%
  mutate(ELS_ID = 
    str_remove(ELS_ID,
               "sub-")
  ) %>%
  mutate(ELS_ID = as.numeric(ELS_ID))
deg_th.2 <-
  deg_th.2  %>%
  mutate(ELS_ID = 
    str_remove(ELS_ID,
               "sub-")
  ) %>%
  mutate(ELS_ID = as.numeric(ELS_ID))
```

## ID to factor
```{r}

deg_th.1 <-
  deg_th.1 %>%
  mutate(ELS_ID = as.factor(ELS_ID))

deg_th.12 <-
  deg_th.12 %>%
  mutate(ELS_ID = as.factor(ELS_ID))

deg_th.14 <-
  deg_th.14 %>%
  mutate(ELS_ID = as.factor(ELS_ID))

deg_th.16 <-
  deg_th.16 %>%
  mutate(ELS_ID = as.factor(ELS_ID))

deg_th.18 <-
  deg_th.18 %>%
  mutate(ELS_ID = as.factor(ELS_ID))

deg_th.2 <-
  deg_th.2 %>%
  mutate(ELS_ID = as.factor(ELS_ID))
```

## renaming variables
```{r}
bg_rois_fp <- "~/Box/Mooddata_Coordinating/1_Lab_Coordinating/Users/JackieSchwartz/PHIND_RS_and_Suicide/April2021Analysis/bn_timeseries_meants/BrainRegions_Brainnetome_250_wBG_rc.xlsx"
bg_rois <- read_excel(bg_rois_fp, col_names = FALSE)

bg_rois <-
  bg_rois %>%
  rename(
    "keep" = "...1",
    "roi" = "...2",
    "bg_name" = "...3",
    "x" = "...4",
    "y" = "...5",
    "z" = "...6"
  )

old_names <- bg_rois$bg_name
oldnames_ch <- dput(as.character(old_names))
new_names <- bg_rois$roi
newnames_ch <- dput(as.character(new_names))

```

### renaming degree
```{r}
#degree th.1
deg_th.1_long <- 
  deg_th.1 %>%
  gather(oldroi_name,deg_value, A8mL:lPFthaR) %>%
  mutate(oldroi_name = factor(oldroi_name))

deg_th.1_long_rename <-
  deg_th.1_long %>%
  mutate(
    newroi_name =
  do.call(fct_recode,
    c(list(oldroi_name), setNames(c(oldnames_ch),c(newnames_ch)))
    )
  )

deg_th.1_wide <-
  deg_th.1_long_rename %>%
  dplyr::select(ELS_ID, newroi_name, deg_value) %>%
  spread(newroi_name, deg_value)

#degree th.12
deg_th.12_long <- 
  deg_th.12 %>%
  gather(oldroi_name,deg_value, A8mL:lPFthaR) %>%
  mutate(oldroi_name = factor(oldroi_name))

deg_th.12_long_rename <-
  deg_th.12_long %>%
  mutate(
    newroi_name =
  do.call(fct_recode,
    c(list(oldroi_name), setNames(c(oldnames_ch),c(newnames_ch)))
    )
  )

deg_th.12_wide <-
  deg_th.12_long_rename %>%
  dplyr::select(ELS_ID, newroi_name, deg_value) %>%
  spread(newroi_name, deg_value)

#degree th.14
deg_th.14_long <- 
  deg_th.14 %>%
  gather(oldroi_name,deg_value, A8mL:lPFthaR) %>%
  mutate(oldroi_name = factor(oldroi_name))

deg_th.14_long_rename <-
  deg_th.14_long %>%
  mutate(
    newroi_name =
  do.call(fct_recode,
    c(list(oldroi_name), setNames(c(oldnames_ch),c(newnames_ch)))
    )
  )

deg_th.14_wide <-
  deg_th.14_long_rename %>%
  dplyr::select(ELS_ID, newroi_name, deg_value) %>%
  spread(newroi_name, deg_value)

#degree th.16
deg_th.16_long <- 
  deg_th.16 %>%
  gather(oldroi_name,deg_value, A8mL:lPFthaR) %>%
  mutate(oldroi_name = factor(oldroi_name))

deg_th.16_long_rename <-
  deg_th.16_long %>%
  mutate(
    newroi_name =
  do.call(fct_recode,
    c(list(oldroi_name), setNames(c(oldnames_ch),c(newnames_ch)))
    )
  )

deg_th.16_wide <-
  deg_th.16_long_rename %>%
  dplyr::select(ELS_ID, newroi_name, deg_value) %>%
  spread(newroi_name, deg_value)

#degree th.18
deg_th.18_long <- 
  deg_th.18 %>%
  gather(oldroi_name,deg_value, A8mL:lPFthaR) %>%
  mutate(oldroi_name = factor(oldroi_name))

deg_th.18_long_rename <-
  deg_th.18_long %>%
  mutate(
    newroi_name =
  do.call(fct_recode,
    c(list(oldroi_name), setNames(c(oldnames_ch),c(newnames_ch)))
    )
  )

deg_th.18_wide <-
  deg_th.18_long_rename %>%
  dplyr::select(ELS_ID, newroi_name, deg_value) %>%
  spread(newroi_name, deg_value)

#degree th.2
deg_th.2_long <- 
  deg_th.2 %>%
  gather(oldroi_name,deg_value, A8mL:lPFthaR) %>%
  mutate(oldroi_name = factor(oldroi_name))

deg_th.2_long_rename <-
  deg_th.2_long %>%
  mutate(
    newroi_name =
  do.call(fct_recode,
    c(list(oldroi_name), setNames(c(oldnames_ch),c(newnames_ch)))
    )
  )

deg_th.2_wide <-
  deg_th.2_long_rename %>%
  dplyr::select(ELS_ID, newroi_name, deg_value) %>%
  spread(newroi_name, deg_value)
```

# appending threshold values to each roi
```{r}
deg_th.1_wide <-
  deg_th.1_wide %>%
  rename_at(
    vars(-ELS_ID),
    function(x)
      paste0(x, "_.10")
    )

deg_th.12_wide <-
  deg_th.12_wide %>%
  rename_at(
    vars(-ELS_ID),
    function(x)
      paste0(x, "_.12")
    )

deg_th.14_wide <-
  deg_th.14_wide %>%
  rename_at(
    vars(-ELS_ID),
    function(x)
      paste0(x, "_.14")
    )

deg_th.16_wide <-
  deg_th.16_wide %>%
  rename_at(
    vars(-ELS_ID),
    function(x)
      paste0(x, "_.16")
    )

deg_th.18_wide <-
  deg_th.18_wide %>%
  rename_at(
    vars(-ELS_ID),
    function(x)
      paste0(x, "_.18")
    )

deg_th.2_wide <-
  deg_th.2_wide %>%
  rename_at(
    vars(-ELS_ID),
    function(x)
      paste0(x, "_.20")
    )
```

# merging files
```{r}
deg_all_thr <-
  left_join(deg_th.1_wide,
            deg_th.12_wide,
            by = "ELS_ID")
deg_all_thr <-
  left_join(deg_all_thr,
            deg_th.14_wide,
            by = "ELS_ID")
deg_all_thr <-
  left_join(deg_all_thr,
            deg_th.16_wide,
            by = "ELS_ID")
deg_all_thr <-
  left_join(deg_all_thr,
            deg_th.18_wide,
            by = "ELS_ID") %>%
  mutate(ELS_ID = factor(ELS_ID))
deg_all_thr <-
  left_join(deg_all_thr,
            deg_th.2_wide,
            by = "ELS_ID")
```

# now do the gathering and spreading
```{r long then wide}
# gather
deg_all_thr_long <- 
  deg_all_thr %>%
  group_by(ELS_ID) %>%
  gather(roi, deg_value, 
         lMFG_L_27_.10:vmPu_R_230_.20) %>%
  separate(col = roi, c("roi", "thresh"), "[.]")
# spread
deg_all_thr_wide <-
  deg_all_thr_long %>%
  spread(thresh, deg_value)  %>%
  mutate(roi = 
           str_sub(roi, 1, str_length(roi)-1)
  )

```

# viz
```{r}
# hist_theme
dist_plot <-
  theme_minimal() +
  theme(
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12)
  )
dist_facet <-
  theme_minimal() +
  theme(
    strip.text = element_text(size = 8),
    axis.text.x = element_text(size = 8, angle = 60, hjust = 1),
    axis.text.y = element_text(size = 8),
    axis.title = element_text(size = 12)
  )
dist_x_labels <-
  theme(
    axis.text.x = element_text(angle = 90,
                               size = 4)
  )
```


```{r dist degree w thresh}
# degree by threshold
dist_deg_by_thresh <- 
  deg_all_thr_long %>%
  mutate(
    thresh = as.factor(thresh)
  ) %>%
  ggplot(.,
         aes(x=roi, y=deg_value)
         ) +
  geom_col(alpha = .5, position = "dodge") +
  scale_y_continuous(labels = function(x) format(x, big.mark = ".", decimal.mark = ",")) +
  dist_plot +
  facet_wrap(~thresh,
             ncol = 2,
             nrow = 4) +
  dist_facet +
    dist_x_labels
dist_deg_by_thresh
```

# area under curve

```{r}
thresh1 <- .10
thresh2 <- .12
thresh3 <- .14
thresh4 <- .16
thresh5 <- .18
thresh6 <- .20
deg_all_thr_wide <-
  deg_all_thr_wide %>%
    rename(.,
           "th.1" = `10`,
           "th.12" = `12`,
           "th.14" = `14`,
           "th.16" = `16`,
           "th.18" = `18`,
           "th.20" = `20`) %>%
  mutate(
    th1toth2 =
      thresh2 - thresh1,
    th2toth3 =
      thresh3 - thresh2,
    th3toth4 =
      thresh4 - thresh3,
    th4toth5 =
      thresh5 - thresh4,
    th5toth6 =
      thresh6 - thresh5
  )
```

Separating ROIs 
options(scipen=999) # turn of sci notation in R
### separating rois
```{r separating rois}
amyg <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi, "Amyg_")
  )
vca <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi, "vCA_")
  )
gpe <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi, "Gpe_")
  )
gpi <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi, "Gpi_")
  )
vmpu <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi, "vmPu_")
  )
nac <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi, "NAC_")
  )
dca <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi, "dCa_")
  )
dlpu <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi, "dlPu_")
  )
cg <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi,"CG_")
  )
fug <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi,"FuG_")
  )
hipp <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi,"Hipp_")
  )
ifg <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi,"IFG_")
  )
ins <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi,"INS_")
  )
ipl <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi,"IPL_")
  )
itg <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi,"ITG_")
  )
locc <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi,"LOcC_")
  )
mfg <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi,"MFG_")
  )
mtg <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi,"MTG_")
  )
mvocc <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi,"MVocC_") 
  )
org <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi,"OrG_")
  )
pcl <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi,"PCL_")
  )
pcun <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi,"Pcun_")
  )
phg <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi,"PhG_")
  )
pog <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
   str_detect(roi,"PoG_")
  )
prg <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi,"PrG_")
  )
psts <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi,"STS_")
  )
sfg <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi,"SFG_")
  )
spl <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi,"SPL_")
  )
stg <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi,"STG_")
  )

mpftha <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi,"mPFtha_")
  )
mpmtha <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi,"mPMtha_")
  )

stha <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi,"Stha_")
  )

rttha <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi,"rTtha_")
  )

pptha <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi,"Pptha_")
  )

otha <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi,"Otha_")
  )

cttha <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi,"cTtha_")
  )

lpftha <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi,"lPFtha_")
  )

sn <- 
  deg_all_thr_wide %>%
  mutate(
    roi = as.factor(roi)
  ) %>%
  filter(
    str_detect(roi,"SN_")
  )
```

### creating aucs
```{r creating amyg auc}
# amyg
amyg_auc <-
  amyg %>%
  mutate(
    amyg_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    amyg_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    amyg_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    amyg_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    amyg_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
amyg_auc$amyg_S_AUCg <-rowSums(amyg_auc[, c("amyg_auc1","amyg_auc2","amyg_auc3","amyg_auc4","amyg_auc5")])

# back to wide format
amyg_auc_wide <-
  amyg_auc %>%
  select(ELS_ID, roi, amyg_S_AUCg) %>%
  spread(roi, amyg_S_AUCg)

```


```{r creating CG auc}
# CG
cg_auc <-
  cg %>%
  mutate(
    cg_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    cg_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    cg_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    cg_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    cg_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
cg_auc$cg_S_AUCg <-rowSums(cg_auc[, c("cg_auc1","cg_auc2","cg_auc3","cg_auc4","cg_auc5")])

# back to wide format
cg_auc_wide <-
  cg_auc %>%
  select(ELS_ID, roi, cg_S_AUCg) %>%
  spread(roi, cg_S_AUCg)

```

```{r creating FuG auc}
# FuG
fug_auc <-
  fug %>%
  mutate(
    fug_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    fug_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    fug_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    fug_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    fug_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
fug_auc$fug_S_AUCg <-rowSums(fug_auc[, c("fug_auc1","fug_auc2","fug_auc3","fug_auc4","fug_auc5")])

# back to wide format
fug_auc_wide <-
  fug_auc %>%
  select(ELS_ID, roi, fug_S_AUCg) %>%
  spread(roi, fug_S_AUCg)
```

```{r creating Hipp auc}
# Hipp
hipp_auc <-
  hipp %>%
  mutate(
    hipp_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    hipp_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    hipp_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    hipp_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    hipp_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
hipp_auc$hipp_S_AUCg <-rowSums(hipp_auc[, c("hipp_auc1","hipp_auc2","hipp_auc3","hipp_auc4","hipp_auc5")])

# back to wide format
hipp_auc_wide <-
  hipp_auc %>%
  select(ELS_ID, roi, hipp_S_AUCg) %>%
  spread(roi, hipp_S_AUCg)
```

```{r creating IFG auc}
# IFG
ifg_auc <-
  ifg %>%
  mutate(
    ifg_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    ifg_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    ifg_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    ifg_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    ifg_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
ifg_auc$ifg_S_AUCg <-rowSums(ifg_auc[, c("ifg_auc1","ifg_auc2","ifg_auc3","ifg_auc4","ifg_auc5")])

# back to wide format
ifg_auc_wide <-
  ifg_auc %>%
  select(ELS_ID, roi, ifg_S_AUCg) %>%
  spread(roi, ifg_S_AUCg)
```

```{r creating INS auc}
# INS
ins_auc <-
  ins %>%
  mutate(
    ins_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    ins_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    ins_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    ins_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    ins_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
ins_auc$ins_S_AUCg <-rowSums(ins_auc[, c("ins_auc1","ins_auc2","ins_auc3","ins_auc4","ins_auc5")])

# back to wide format
ins_auc_wide <-
  ins_auc %>%
  select(ELS_ID, roi, ins_S_AUCg) %>%
  spread(roi, ins_S_AUCg)
```

```{r creating IPL auc}
# IPL
ipl_auc <-
  ipl %>%
  mutate(
    ipl_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    ipl_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    ipl_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    ipl_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    ipl_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
ipl_auc$ipl_S_AUCg <-rowSums(ipl_auc[, c("ipl_auc1","ipl_auc2","ipl_auc3","ipl_auc4","ipl_auc5")])

# back to wide format
ipl_auc_wide <-
  ipl_auc %>%
  select(ELS_ID, roi, ipl_S_AUCg) %>%
  spread(roi, ipl_S_AUCg)
```

```{r creating ITG auc}
# ITG
itg_auc <-
  itg %>%
  mutate(
    itg_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    itg_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    itg_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    itg_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    itg_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
itg_auc$itg_S_AUCg <-rowSums(itg_auc[, c("itg_auc1","itg_auc2","itg_auc3","itg_auc4","itg_auc5")])

# back to wide format
itg_auc_wide <-
  itg_auc %>%
  select(ELS_ID, roi, itg_S_AUCg) %>%
  spread(roi, itg_S_AUCg)
```

```{r creating LOcC auc}
# LOcC
locc_auc <-
  locc %>%
  mutate(
    locc_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    locc_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    locc_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    locc_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    locc_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
locc_auc$locc_S_AUCg <-rowSums(locc_auc[, c("locc_auc1","locc_auc2","locc_auc3","locc_auc4","locc_auc5")])

# back to wide format
locc_auc_wide <-
  locc_auc %>%
  select(ELS_ID, roi, locc_S_AUCg) %>%
  spread(roi, locc_S_AUCg)
```


```{r creating MFG auc}
# MFG
mfg_auc <-
  mfg %>%
  mutate(
    mfg_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    mfg_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    mfg_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    mfg_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    mfg_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
mfg_auc$mfg_S_AUCg <-rowSums(mfg_auc[, c("mfg_auc1","mfg_auc2","mfg_auc3","mfg_auc4","mfg_auc5")])

# back to wide format
mfg_auc_wide <-
  mfg_auc %>%
  select(ELS_ID, roi, mfg_S_AUCg) %>%
  spread(roi, mfg_S_AUCg)
```

```{r creating MTG auc}
# MTG
mtg_auc <-
  mtg %>%
  mutate(
    mtg_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    mtg_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    mtg_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    mtg_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    mtg_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
mtg_auc$mtg_S_AUCg <-rowSums(mtg_auc[, c("mtg_auc1","mtg_auc2","mtg_auc3","mtg_auc4","mtg_auc5")])

# back to wide format
mtg_auc_wide <-
  mtg_auc %>%
  select(ELS_ID, roi, mtg_S_AUCg) %>%
  spread(roi, mtg_S_AUCg)
```


```{r creating MVocC auc}
# MVocC
mvocc_auc <-
  mvocc %>%
  mutate(
    mvocc_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    mvocc_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    mvocc_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    mvocc_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    mvocc_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
mvocc_auc$mvocc_S_AUCg <-rowSums(mvocc_auc[, c("mvocc_auc1","mvocc_auc2","mvocc_auc3","mvocc_auc4","mvocc_auc5")])

# back to wide format
mvocc_auc_wide <-
  mvocc_auc %>%
  select(ELS_ID, roi, mvocc_S_AUCg) %>%
  spread(roi, mvocc_S_AUCg)
```

```{r creating OrG auc}
# OrG
org_auc <-
  org %>%
  mutate(
    org_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    org_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    org_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    org_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    org_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
org_auc$org_S_AUCg <-rowSums(org_auc[, c("org_auc1","org_auc2","org_auc3","org_auc4","org_auc5")])

# back to wide format
org_auc_wide <-
  org_auc %>%
  select(ELS_ID, roi, org_S_AUCg) %>%
  spread(roi, org_S_AUCg)
```

```{r creating PCL auc}
# PCL
pcl_auc <-
  pcl %>%
  mutate(
    pcl_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    pcl_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    pcl_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    pcl_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    pcl_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
pcl_auc$pcl_S_AUCg <-rowSums(pcl_auc[, c("pcl_auc1","pcl_auc2","pcl_auc3","pcl_auc4","pcl_auc5")])

# back to wide format
pcl_auc_wide <-
  pcl_auc %>%
  select(ELS_ID, roi, pcl_S_AUCg) %>%
  spread(roi, pcl_S_AUCg)
```

```{r creating Pcun auc}
# Pcun
pcun_auc <-
  pcun %>%
  mutate(
    pcun_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    pcun_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    pcun_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    pcun_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    pcun_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
pcun_auc$pcun_S_AUCg <-rowSums(pcun_auc[, c("pcun_auc1","pcun_auc2","pcun_auc3","pcun_auc4","pcun_auc5")])

# back to wide format
pcun_auc_wide <-
  pcun_auc %>%
  select(ELS_ID, roi, pcun_S_AUCg) %>%
  spread(roi, pcun_S_AUCg)
```

```{r creating PhG auc}
# PhG
phg_auc <-
  phg %>%
  mutate(
    phg_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    phg_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    phg_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    phg_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    phg_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
phg_auc$phg_S_AUCg <-rowSums(phg_auc[, c("phg_auc1","phg_auc2","phg_auc3","phg_auc4","phg_auc5")])

# back to wide format
phg_auc_wide <-
  phg_auc %>%
  select(ELS_ID, roi, phg_S_AUCg) %>%
  spread(roi, phg_S_AUCg)
```

```{r creating PoG auc}
# PoG
pog_auc <-
  pog %>%
  mutate(
    pog_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    pog_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    pog_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    pog_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    pog_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
pog_auc$pog_S_AUCg <-rowSums(pog_auc[, c("pog_auc1","pog_auc2","pog_auc3","pog_auc4","pog_auc5")])

# back to wide format
pog_auc_wide <-
  pog_auc %>%
  select(ELS_ID, roi, pog_S_AUCg) %>%
  spread(roi, pog_S_AUCg)
```

```{r creating PrG auc}
# PrG
prg_auc <-
  prg %>%
  mutate(
    prg_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    prg_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    prg_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    prg_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    prg_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
prg_auc$prg_S_AUCg <-rowSums(prg_auc[, c("prg_auc1","prg_auc2","prg_auc3","prg_auc4","prg_auc5")])

# back to wide format
prg_auc_wide <-
  prg_auc %>%
  select(ELS_ID, roi, prg_S_AUCg) %>%
  spread(roi, prg_S_AUCg)
```

```{r creating pSTS auc}
# pSTS
psts_auc <-
  psts %>%
  mutate(
    psts_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    psts_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    psts_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    psts_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    psts_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
psts_auc$psts_S_AUCg <-rowSums(psts_auc[, c("psts_auc1","psts_auc2","psts_auc3","psts_auc4","psts_auc5")])

# back to wide format
psts_auc_wide <-
  psts_auc %>%
  select(ELS_ID, roi, psts_S_AUCg) %>%
  spread(roi, psts_S_AUCg)
```

```{r creating SFG auc}
# SFG
sfg_auc <-
  sfg %>%
  mutate(
    sfg_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    sfg_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    sfg_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    sfg_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    sfg_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
sfg_auc$sfg_S_AUCg <-rowSums(sfg_auc[, c("sfg_auc1","sfg_auc2","sfg_auc3","sfg_auc4","sfg_auc5")])

# back to wide format
sfg_auc_wide <-
  sfg_auc %>%
  select(ELS_ID, roi, sfg_S_AUCg) %>%
  spread(roi, sfg_S_AUCg)
```

```{r creating SPL auc}
# SPL
spl_auc <-
  spl %>%
  mutate(
    spl_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    spl_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    spl_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    spl_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    spl_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
spl_auc$spl_S_AUCg <-rowSums(spl_auc[, c("spl_auc1","spl_auc2","spl_auc3","spl_auc4","spl_auc5")])

# back to wide format
spl_auc_wide <-
  spl_auc %>%
  select(ELS_ID, roi, spl_S_AUCg) %>%
  spread(roi, spl_S_AUCg)
```

```{r creating STG auc}
# STG
stg_auc <-
  stg %>%
  mutate(
    stg_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    stg_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    stg_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    stg_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    stg_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
stg_auc$stg_S_AUCg <-rowSums(stg_auc[, c("stg_auc1","stg_auc2","stg_auc3","stg_auc4","stg_auc5")])

# back to wide format
stg_auc_wide <-
  stg_auc %>%
  select(ELS_ID, roi, stg_S_AUCg) %>%
  spread(roi, stg_S_AUCg)
```

```{r creating CTtha}
# CTtha
cttha_auc <-
  cttha %>%
  mutate(
    cttha_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    cttha_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    cttha_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    cttha_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    cttha_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
cttha_auc$cttha_S_AUCg <-rowSums(cttha_auc[, c("cttha_auc1","cttha_auc2","cttha_auc3","cttha_auc4","cttha_auc5")])  

# back to wide format
cttha_auc_wide <-
  cttha_auc %>%
  select(ELS_ID, roi, cttha_S_AUCg) %>%
  spread(roi, cttha_S_AUCg)
```

```{r dCa}
# dCa
dca_auc <-
  dca %>%
  mutate(
    dca_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    dca_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    dca_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    dca_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    dca_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
dca_auc$dca_S_AUCg <-rowSums(dca_auc[, c("dca_auc1","dca_auc2","dca_auc3","dca_auc4","dca_auc5")])  

# back to wide format
dca_auc_wide <-
  dca_auc %>%
  select(ELS_ID, roi, dca_S_AUCg) %>%
  spread(roi, dca_S_AUCg)
```

```{r dlPu}
# dlPu

dlpu_auc <-
  dlpu %>%
  mutate(
    dlpu_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    dlpu_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    dlpu_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    dlpu_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    dlpu_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
dlpu_auc$dlpu_S_AUCg <-rowSums(dlpu_auc[, c("dlpu_auc1","dlpu_auc2","dlpu_auc3","dlpu_auc4","dlpu_auc5")])

# back to wide format
dlpu_auc_wide <-
  dlpu_auc %>%
  select(ELS_ID, roi, dlpu_S_AUCg) %>%
  spread(roi, dlpu_S_AUCg)
```

```{r Gpe}
# Gpe
gpe_auc <-
  gpe %>%
  mutate(
    gpe_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    gpe_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    gpe_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    gpe_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    gpe_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
gpe_auc$gpe_S_AUCg <-rowSums(gpe_auc[, c("gpe_auc1","gpe_auc2","gpe_auc3","gpe_auc4","gpe_auc5")])  

# back to wide format
gpe_auc_wide <-
  gpe_auc %>%
  select(ELS_ID, roi, gpe_S_AUCg) %>%
  spread(roi, gpe_S_AUCg)
```

```{r Gpi}
# Gpi
gpi_auc <-
  gpi %>%
  mutate(
    gpi_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    gpi_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    gpi_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    gpi_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    gpi_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
gpi_auc$gpi_S_AUCg <-rowSums(gpi_auc[, c("gpi_auc1","gpi_auc2","gpi_auc3","gpi_auc4","gpi_auc5")]) 

# back to wide format
gpi_auc_wide <-
  gpi_auc %>%
  select(ELS_ID, roi, gpi_S_AUCg) %>%
  spread(roi, gpi_S_AUCg)
```

```{r lPFtha}
# lpftha
lpftha_auc <-
  lpftha %>%
  mutate(
    lpftha_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    lpftha_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    lpftha_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    lpftha_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    lpftha_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
lpftha_auc$lpftha_S_AUCg <-rowSums(lpftha_auc[, c("lpftha_auc1","lpftha_auc2","lpftha_auc3","lpftha_auc4","lpftha_auc5")]) 

# back to wide format
lpftha_auc_wide <-
  lpftha_auc %>%
  select(ELS_ID, roi, lpftha_S_AUCg) %>%
  spread(roi, lpftha_S_AUCg)
```

```{r mPFtha}
# mPFtha
mpftha_auc <-
  mpftha %>%
  mutate(
    mpftha_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    mpftha_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    mpftha_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    mpftha_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    mpftha_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
mpftha_auc$mpftha_S_AUCg <-rowSums(mpftha_auc[, c("mpftha_auc1","mpftha_auc2","mpftha_auc3","mpftha_auc4","mpftha_auc5")]) 

# back to wide format
mpftha_auc_wide <-
  mpftha_auc %>%
  select(ELS_ID, roi, mpftha_S_AUCg) %>%
  spread(roi, mpftha_S_AUCg)
```

```{r mPMtha}
# mPMtha
mpmtha_auc <-
  mpmtha %>%
  mutate(
    mpmtha_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    mpmtha_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    mpmtha_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    mpmtha_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    mpmtha_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
mpmtha_auc$mpmtha_S_AUCg <-rowSums(mpmtha_auc[, c("mpmtha_auc1","mpmtha_auc2","mpmtha_auc3","mpmtha_auc4","mpmtha_auc5")]) 

# back to wide format
mpmtha_auc_wide <-
  mpmtha_auc %>%
  select(ELS_ID, roi, mpmtha_S_AUCg) %>%
  spread(roi, mpmtha_S_AUCg)
```

```{r NAC}
# NAC
nac_auc <-
  nac %>%
  mutate(
    nac_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    nac_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    nac_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    nac_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    nac_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
nac_auc$nac_S_AUCg <-rowSums(nac_auc[, c("nac_auc1","nac_auc2","nac_auc3","nac_auc4","nac_auc5")]) 

# back to wide format
nac_auc_wide <-
  nac_auc %>%
  select(ELS_ID, roi, nac_S_AUCg) %>%
  spread(roi, nac_S_AUCg)
```

```{r Otha}
# Otha
otha_auc <-
  otha %>%
  mutate(
    otha_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    otha_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    otha_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    otha_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    otha_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
otha_auc$otha_S_AUCg <-rowSums(otha_auc[, c("otha_auc1","otha_auc2","otha_auc3","otha_auc4","otha_auc5")]) 
# back to wide format
otha_auc_wide <-
  otha_auc %>%
  select(ELS_ID, roi, otha_S_AUCg) %>%
  spread(roi, otha_S_AUCg)
```


```{r Pptha}
# Pptha
pptha_auc <-
  pptha %>%
  mutate(
    pptha_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    pptha_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    pptha_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    pptha_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    pptha_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
pptha_auc$pptha_S_AUCg <-rowSums(pptha_auc[, c("pptha_auc1","pptha_auc2","pptha_auc3","pptha_auc4","pptha_auc5")]) 

# back to wide format
pptha_auc_wide <-
  pptha_auc %>%
  select(ELS_ID, roi, pptha_S_AUCg) %>%
  spread(roi, pptha_S_AUCg)
```

```{r rTtha}
# rTtha
rttha_auc <-
  rttha %>%
  mutate(
    rttha_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    rttha_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    rttha_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    rttha_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    rttha_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
rttha_auc$rttha_S_AUCg <-rowSums(rttha_auc[, c("rttha_auc1","rttha_auc2","rttha_auc3","rttha_auc4","rttha_auc5")]) 

# back to wide format
rttha_auc_wide <-
  rttha_auc %>%
  select(ELS_ID, roi, rttha_S_AUCg) %>%
  spread(roi, rttha_S_AUCg)
```

```{r Stha}
# Stha
stha_auc <-
  stha %>%
  mutate(
    stha_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    stha_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    stha_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    stha_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    stha_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
stha_auc$stha_S_AUCg <-rowSums(stha_auc[, c("stha_auc1","stha_auc2","stha_auc3","stha_auc4","stha_auc5")])

# back to wide format
stha_auc_wide <-
  stha_auc %>%
  select(ELS_ID, roi, stha_S_AUCg) %>%
  spread(roi, stha_S_AUCg)
```

```{r vCA}
# vCA
vca_auc <-
  vca %>%
  mutate(
    vca_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    vca_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    vca_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    vca_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    vca_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
vca_auc$vca_S_AUCg <-rowSums(vca_auc[, c("vca_auc1","vca_auc2","vca_auc3","vca_auc4","vca_auc5")]) 

# back to wide format
vca_auc_wide <-
  vca_auc %>%
  select(ELS_ID, roi, vca_S_AUCg) %>%
  spread(roi, vca_S_AUCg)
```

```{r vmPu}
# vmPu
vmpu_auc <-
  vmpu %>%
  mutate(
    vmpu_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    vmpu_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    vmpu_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    vmpu_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    vmpu_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
vmpu_auc$vmpu_S_AUCg <-rowSums(vmpu_auc[, c("vmpu_auc1","vmpu_auc2","vmpu_auc3","vmpu_auc4","vmpu_auc5")])

# back to wide format
vmpu_auc_wide <-
  vmpu_auc %>%
  select(ELS_ID, roi, vmpu_S_AUCg) %>%
  spread(roi, vmpu_S_AUCg)
```

```{r SN}
# SN
sn_auc <-
  sn %>%
  mutate(
    sn_auc1 = th1toth2 * ((th.1 + th.12) / 2),
    sn_auc2 = th2toth3 * ((th.12 + th.14) / 2),
    sn_auc3 = th3toth4 * ((th.14 + th.16) / 2),
    sn_auc4 = th4toth5 * ((th.16 + th.18) / 2),
    sn_auc5 = th5toth6 * ((th.18 + th.20) / 2)
  ) %>%
  ungroup(ELS_ID) %>%
  mutate(ELS_ID = as.factor(ELS_ID))
sn_auc$sn_S_AUCg <-rowSums(sn_auc[, c("sn_auc1","sn_auc2","sn_auc3","sn_auc4","sn_auc5")]) 

# back to wide format
sn_auc_wide <-
  sn_auc %>%
  select(ELS_ID, roi, sn_S_AUCg) %>%
  spread(roi, sn_S_AUCg)
```

# joinging roi dfs
```{r}
deg_aucs <-
  left_join(amyg_auc_wide,
            cg_auc_wide,
            by = "ELS_ID") 
deg_aucs <-
  left_join(deg_aucs,
            fug_auc_wide,
            by = "ELS_ID") 
deg_aucs <-
  left_join(deg_aucs,
            hipp_auc_wide,
            by = "ELS_ID") 
deg_aucs <-
  left_join(deg_aucs,
            ifg_auc_wide,
            by = "ELS_ID") 
deg_aucs <-
  left_join(deg_aucs,
           ins_auc_wide,
            by = "ELS_ID") 
deg_aucs <-
  left_join(deg_aucs,
           ipl_auc_wide,
            by = "ELS_ID") 
deg_aucs <-
  left_join(deg_aucs,
           itg_auc_wide,
            by = "ELS_ID") 
deg_aucs <-
  left_join(deg_aucs,
           locc_auc_wide,
            by = "ELS_ID") 
deg_aucs <-
  left_join(deg_aucs,
           mfg_auc_wide,
            by = "ELS_ID") 
deg_aucs <-
  left_join(deg_aucs,
            mtg_auc_wide,
            by = "ELS_ID") 
deg_aucs <-
  left_join(deg_aucs,
           mvocc_auc_wide,
            by = "ELS_ID") 
deg_aucs <-
  left_join(deg_aucs,
           org_auc_wide,
            by = "ELS_ID") 
deg_aucs <-
  left_join(deg_aucs,
           pcl_auc_wide,
            by = "ELS_ID") 
deg_aucs <-
  left_join(deg_aucs,
           pcun_auc_wide,
            by = "ELS_ID") 
deg_aucs <-
  left_join(deg_aucs,
           phg_auc_wide,
            by = "ELS_ID") 
deg_aucs <-
  left_join(deg_aucs,
           pog_auc_wide,
            by = "ELS_ID") 
deg_aucs <-
  left_join(deg_aucs,
           prg_auc_wide,
            by = "ELS_ID") 
deg_aucs <-
  left_join(deg_aucs,
           psts_auc_wide,
            by = "ELS_ID") 
deg_aucs <-
  left_join(deg_aucs,
           sfg_auc_wide,
            by = "ELS_ID") 
deg_aucs <-
  left_join(deg_aucs,
           spl_auc_wide,
            by = "ELS_ID") 
deg_aucs <-
  left_join(deg_aucs,
           stg_auc_wide,
            by = "ELS_ID")
deg_aucs <-
  left_join(deg_aucs,
           cttha_auc_wide,
            by = "ELS_ID")
deg_aucs <-
  left_join(deg_aucs,
           dca_auc_wide,
            by = "ELS_ID")
deg_aucs <-
  left_join(deg_aucs,
           dlpu_auc_wide,
            by = "ELS_ID")
deg_aucs <-
  left_join(deg_aucs,
           gpe_auc_wide,
            by = "ELS_ID")
deg_aucs <-
  left_join(deg_aucs,
           gpi_auc_wide,
            by = "ELS_ID")
deg_aucs <-
  left_join(deg_aucs,
           lpftha_auc_wide,
            by = "ELS_ID")
deg_aucs <-
  left_join(deg_aucs,
           mpftha_auc_wide,
            by = "ELS_ID")
deg_aucs <-
  left_join(deg_aucs,
           mpmtha_auc_wide,
            by = "ELS_ID")
deg_aucs <-
  left_join(deg_aucs,
           nac_auc_wide,
            by = "ELS_ID")
deg_aucs <-
  left_join(deg_aucs,
           otha_auc_wide,
            by = "ELS_ID")
deg_aucs <-
  left_join(deg_aucs,
           pptha_auc_wide,
            by = "ELS_ID")
deg_aucs <-
  left_join(deg_aucs,
           rttha_auc_wide,
            by = "ELS_ID")
deg_aucs <-
  left_join(deg_aucs,
           stha_auc_wide,
            by = "ELS_ID")
deg_aucs <-
  left_join(deg_aucs,
           vca_auc_wide,
            by = "ELS_ID")
deg_aucs <-
  left_join(deg_aucs,
           vmpu_auc_wide,
            by = "ELS_ID")
deg_aucs <-
  left_join(deg_aucs,
           sn_auc_wide,
            by = "ELS_ID")
```

```{r}
deg_aucs_select <-
  deg_aucs %>%
  rename_at(
    vars(-ELS_ID),
    function(x)
      paste0(x, ".deg")
    )
```

### write csv
```{r}
deg_aucs_select_fp <-"~/Box/Mooddata_Coordinating/1_Lab_Coordinating/Users/JackieSchwartz/PHIND_RS_and_Suicide/April2021Analysis/deg_aucs.csv"
write_csv(deg_aucs_select,deg_aucs_select_fp)
```
