---
title: "graph_t1_corrrs"
author: "Jackie"
date: "10/22/2020"
output: html_notebook
---

Understanding correlations among local graph metrics (5)

# Loading libraries
```{r,echo=FALSE,results='hide',message=FALSE}
library(tidyverse)
library(haven)
library(modelr)
library(readxl)
library(Rcpp)
library(httpuv)
library(shiny)
library(plotly)
library(corrr)
library(seriation)
library(d3heatmap)
library(heatmaply)
library(corrplot)
```

# Read in data

### filepaths
```{r, echo=FALSE,results='hide', message=FALSE}
degree_fp <- "~/Box/Mooddata_Coordinating/1_Lab_Coordinating/Users/JackieSchwartz/PHIND_RS_and_Suicide/Octo2020Analysis/deg_aucs.csv"
effic_loc_fp <- "~/Box/Mooddata_Coordinating/1_Lab_Coordinating/Users/JackieSchwartz/PHIND_RS_and_Suicide/Octo2020Analysis/eff_loc_aucs.csv"
eig_cent_fp <- "~/Box/Mooddata_Coordinating/1_Lab_Coordinating/Users/JackieSchwartz/PHIND_RS_and_Suicide/Octo2020Analysis/eig_cent_aucs.csv"
part_coeff_fp <- "~/Box/Mooddata_Coordinating/1_Lab_Coordinating/Users/JackieSchwartz/PHIND_RS_and_Suicide/Octo2020Analysis/pc_aucs.csv"
within_mod_zscore_fp <- "~/Box/Mooddata_Coordinating/1_Lab_Coordinating/Users/JackieSchwartz/PHIND_RS_and_Suicide/Octo2020Analysis/wm_z_aucs.csv"
```

## reading in
```{r, echo=FALSE,results='hide',message=FALSE}

degree <- read_csv(degree_fp) %>%
  mutate(ELS_ID = factor(ELS_ID))
effic_loc <- read_csv(effic_loc_fp) %>%
  mutate(ELS_ID = factor(ELS_ID))
eig_cent <- read_csv(eig_cent_fp) %>%
  mutate(ELS_ID = factor(ELS_ID))
part_coeff <- read_csv(part_coeff_fp) %>%
  mutate(ELS_ID = factor(ELS_ID))
within_mod_zscore <- read_csv(within_mod_zscore_fp) %>%
  mutate(ELS_ID = factor(ELS_ID))
```

# joining dataframes
```{r,echo=FALSE,results='hide'}
graph_all <-
  left_join(
    effic_loc,
    degree,
    by = "ELS_ID"
  )
graph_all <-
  left_join(
    graph_all,
    eig_cent,
    by = "ELS_ID"
  )
graph_all <-
  left_join(
    graph_all,
    part_coeff,
    by = "ELS_ID"
  )
graph_all <-
  left_join(
    graph_all,
    within_mod_zscore,
    by = "ELS_ID"
  ) %>%
  filter(ELS_ID != "8")
  
```


unusable data including signal dropout - 6, 35, 173, 63, 173, 199, 211, 180

withdrew - 7, 8, 200

no scan - 27, 44, 52, 66, 71, 78, 82, 84, 94, 96, 105, 128, 131, 133, 141, 177, 190, 198, 203, 206, 207, 209

motion flagged - 11, 20, 43, 80, 130, 149, 216, 194

```{r}
sigdrpout <- factor(c("6", "35", "173", "63", "173", "199", "211", "180"))
witdrew <- factor(c("7", "8", "200"))
motflagged <- factor(c("11", "20", "43", "80", "130", "149", "216", "194"))
graph_all_filt <- 
  graph_all %>%
  mutate(
    signaldrop = ifelse(ELS_ID %in% sigdrpout, 1, 0),
    withdrew = ifelse(ELS_ID %in% witdrew, 1, 0),
    mot = ifelse(ELS_ID %in% motflagged, 1, 0),
    drop = ifelse(signaldrop == 1 | withdrew == 1 | mot == 1,
                  1,
                  0)
  ) %>%
  dplyr::select(ELS_ID, signaldrop, withdrew, mot, drop, everything())

graph_all_filt_final <- 
  graph_all_filt %>%
  filter(drop == 0) %>%
  dplyr::select(-signaldrop, -withdrew, -mot, -drop)
  
```

## write csv
```{r}
graph_all_fp <- "~/Box/Mooddata_Coordinating/1_Lab_Coordinating/Users/JackieSchwartz/PHIND_RS_and_Suicide/Octo2020Analysis/graph_all.csv"
write_csv(graph_all_filt_final, graph_all_fp)
```
# Correlatons within each metric
__more local properties__  
__degree:__ _num of edges connected to a node_  
__local efficiency:__ _global efficiency computed on node neighborhoods;_     
_reflects efficient information transfer in the immediate neighborhood of each node;_      
_how well information is exchanged by a node’s neghbors when it is removed_  
__eigenvector centrality:__ _determines relative importance of nodes_  
__within-mod z score:__ _z socre of a node's within-module degree; z-scores_    
_greater than 2.5 denote hub status_
__participation coefficient:__ _hubs refer to nodes with high nodal centrality_  
_If a node's edges are entirley restricted to its community, it's pc is zero._  
_Lower pc values indicate provincial hub status._
_If the node's edges are evenely distributed among all communityes, the pc increases._  
_Higher pc values indicate connector hub status._  

## degree
```{r degree}
deg_roi_aucs_cor <- 
  graph_all %>%
  select(
    ends_with("deg")
    ) %>%
  cor()

deg_cor_tbl <- 
  graph_all %>%
  select(
    ends_with("deg")
  ) %>% 
  correlate(use = "complete.obs", method = "spearman") %>% 
  fashion()
deg_cor_tbl

#d3heatmap(deg_roi_aucs, scale = "column", hclustfun = hclust, dendrogram = "none")
png(height=2000, width=2000, file="deg_corrplot.png")
corrplot(deg_roi_aucs_cor, 
         method = "color",
         order = "hclust", 
         tl.cex = .6, 
         tl.col = "black",
         type = "upper")
dev.off()

```

## local efficiency
```{r loc eff}
loc_eff_roi_aucs_cor <- 
  graph_all %>%
  select(
    ends_with("eff_loc")
    ) %>%
  cor()

loc_eff_cor_tbl <- 
  graph_all %>%
  select(
    ends_with("eff_loc")
  ) %>% 
  correlate(use = "complete.obs", method = "spearman") %>% 
  fashion()
loc_eff_cor_tbl

png(height=2000, width=2000, file="loceff_corrplot.png")
corrplot(loc_eff_roi_aucs_cor, method = "color",
         order = "hclust",
         tl.cex = .6, 
         tl.col = "black", 
         type = "upper")
dev.off()
```

## eigenvector centrality
```{r eig cent}
eig_cent_roi_aucs_cor <- 
  graph_all %>%
  select(
    ends_with("eig_cent")
    ) %>%
  cor()

eig_cent_cor_tbl <- 
  graph_all %>%
  select(
    ends_with("eig_cent")
  ) %>% 
  correlate(use = "complete.obs", method = "spearman") %>% 
  fashion()
eig_cent_cor_tbl

png(height=2000, width=2000, file="eigcent_corrplot.png")
corrplot(eig_cent_roi_aucs_cor, 
         method = "color",
         order = "hclust",
         tl.cex = .6, 
         tl.col = "black", 
         type = "upper")
dev.off()
```

## within module z score 
```{r within mod}
wm_z_aucs_cor <- 
  graph_all %>%
  select(
    ends_with("wm_z")
    ) %>%
  cor()

wm_z_cor_tbl <- 
  graph_all %>%
  select(
    ends_with("wm_z")
  ) %>% 
  correlate(use = "complete.obs", method = "spearman") %>% 
  fashion()
wm_z_cor_tbl

png(height=2000, width=2000, file="wm_z_corrplot.png")
corrplot(wm_z_aucs_cor, 
         method = "color",
         order = "hclust",
         tl.cex = .6, 
         tl.col = "black", 
         type = "upper")
dev.off()
```

## participation coefficient 
```{r part coeff}
pc_aucs_cor <- 
  graph_all %>%
  select(
    ends_with("pc")
    ) %>%
  cor()

pc_cor_tbl <- 
  graph_all %>%
  select(
    ends_with("pc")
  ) %>% 
  correlate(use = "complete.obs", method = "spearman") %>% 
  fashion()
pc_cor_tbl

png(height=2000, width=2000, file="pc_corrplot.png")
corrplot(pc_aucs_cor, 
         method = "color",
         order = "hclust",
         tl.cex = .6, 
         tl.col = "black", 
         type = "upper")
dev.off()
```


# correlation matrix among all variables
```{r}
aucs_cor <- 
  graph_all %>%
  select(-ELS_ID) %>%
  cor()

cor_tbl <- 
  graph_all %>%
  select(-ELS_ID) %>% 
  correlate(use = "complete.obs", method = "spearman") %>% 
  fashion()
cor_tbl

png(height=2000, width=2000, file="all_corrplot.png")
corrplot(aucs_cor, 
         diag = FALSE,
         insig = "blank",
         method = "color",
         order = "FPC",
         tl.pos = "td",
         tl.cex = .1, 
         tl.col = "black", 
         tl.offset = .6,
         type = "upper")
dev.off()
```

