---
title: "siq"
author: "Jackie"
date: "5/24/2020"
output: html_notebook
---

Data structure: SI information based on the Suicidal Ideation Questionnaire-JR (Reynolds, 1987) 
- 15 items ranging from 0 - 6 (higher score = higher severity)
- For total, sum scores for 15 items, for total possible score of 90

Purpose: To identify which "family" fits my response variable (the SIQ) best for elastic net.


# Loading libraries
```{r, message=FALSE}
library(tidyverse)
library(haven)
library(modelr)
library(readxl)
library(Rcpp)
library(httpuv)
library(corrr)
library(seriation)
library(d3heatmap)
library(heatmaply)
library(corrplot)
library(haven)
library(naniar)
library(brms)
library(rstan)
library(bayesplot)
library(rstanarm)
library(knitr)
library(loo)
library(nonnest2)
```

# filepaths
```{r, echo=FALSE, message=FALSE}
siq_t3_fp <- "~/Box/siq.T3.csv"
graph_fp <- "~/Box/graph_all.csv"
```

# reading in files
```{r, echo=FALSE, message=FALSE}
siq_t3 <- read_csv(siq_t3_fp)  %>%
  mutate(ELS_ID = factor(ELS_ID))

graph <- read_csv(graph_fp) %>%
  mutate(ELS_ID = factor(ELS_ID))
```

# score siq data

### filtering out duplicated IDs 
_I'm using the .5/.2 sessions bc they are closest to the scan date_
```{r}
siq_t3_dup <- siq_t3 %>%
  filter(duplicated(ELS_ID)
         ) # duplicated IDs

siq_t3_clean <- siq_t3 %>%
  mutate(reassessed =
           ifelse(is.na(Session_Type),
                  "no",
                  "yes"
           )
  )

siq_t3_clean_unique <- siq_t3_clean %>%
  filter(!("xx" & 
           is.na(Session_Type)
           )
         ) %>%
    filter(!("xx" &
               is.na(Session_Type)
             )
           )

```

## recoding 999s and 888s
```{r}
vars <- c("siq_1.T3", "siq_2.T3", "siq_3.T3",  "siq_4.T3", "siq_5.T3", "siq_6.T3", "siq_7.T3", "siq_8.T3", "siq_9.T3", "siq_10.T3", "siq_11.T3", "siq_12.T3", "siq_13.T3", "siq_14.T3", "siq_15.T3")

siq_t3_clean_unique <- 
  siq_t3_clean_unique %>%
  replace_with_na_at(.,
                     .vars = vars,
                     condition = ~.x == 999) %>%
  dplyr::select(-SIQ_total.T3, -reassessed)

```

## scoring siq total
```{r}
siq_t3_clean_total <-
  siq_t3_clean_unique %>%
  mutate(
    siq_total.T3 = 
      rowSums(siq_t3_clean_unique[,(which(names(siq_t3_clean_unique)=='siq_1.T3'):which(names(siq_t3_clean_unique)=='siq_15.T3'))])
  ) %>%
  drop_na(siq_total.T3) %>%
  mutate(ELS_ID = factor(ELS_ID))
```

### cronbach's alpha
```{r}
library(cocron)
siq_t3_alpha <- siq_t3_clean_total %>%
  dplyr::select(siq_1.T3:siq_15.T3)

cronbach.alpha(siq_t3_alpha, standardized = T)
# alpha 
# 0.96098 
```

### merging SI and brain data
```{r}
siq_graph <- left_join(graph, siq_t3_clean_total,
                       by = "ELS_ID") %>%
  drop_na(siq_total.T3)

# 114 individuals with SIQ at T3 (13 of which do not have usable brain data at T1)
# 173 individuals with brain data at T1

siq_graph_fp <- "~/Box/siq_graph.csv"
write_csv(siq_graph, siq_graph_fp)
```


# data viz
```{r}
siq_graph_plot <- siq_graph %>% 
 dplyr::select(ELS_ID, siq_total.T3) %>%
  ggplot(.,
         aes(x=siq_total.T3)) +
  geom_histogram(bins = 25, position = "identity", alpha = .5) +
  scale_x_continuous(breaks = seq(from = 0, to = 70, by = 5), 
                     name = "SIQ Scores") +
  scale_y_continuous(breaks = seq(from = 0, to = 50, by = 5)) +
  ggtitle("Distribution of suicidal ideation") +
  theme_light()
ggsave("siq_graph.jpg", siq_graph_plot, width = 7, height = 5)
```
#### summary table
```{r}
# Create the function for mode
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}

siq_sum_table <-
  siq_graph %>% 
  summarize(
    mean_si = mean(siq_total.T3),
    median_si = median(siq_total.T3),
    mode_si = getmode(siq_total.T3),
    min_si = min(siq_total.T3),
    max_si = max(siq_total.T3),
    n = n()
    )

```


__Bayesian Regression Model using 'Stan' (brms)__ Package to see which distribution fits my response data (SIQ) the best.

## What is the proportion of zeros in my response data?
```{r, message=FALSE}
# creating function to get proportion of zero
prop_zero <- function(x) mean(x == 0)


prop_zero(siq_graph$siq_total.T3) # check proportion of zeros in y
# 0.1188119

```

> There are approx. 11.9% of zeros in my response data (SIQ)

## using brm to see which distribution fits SIQ in my data the best

### poisson
```{r, message=FALSE}
# poisson
fit_p <- brm(siq_total.T3 ~ 1, data = siq_graph, family = poisson()) 
summary(fit_p)
fit_p <- add_criterion(fit_p, c("loo", "kfold", "waic"))
l_fit_p <- loo(fit_p, save_psis = TRUE, k_threshold = 0.7) # the importance sampling method we used is psis =  Pareto-Smoothed Importance Sampling 
# k_threshold = Threshold for flagging estimates of the Pareto shape parameters ð‘˜ estimated by loo
pareto_k_table(l_fit_p)
plot(l_fit_p, diagnotic="k")
print(l_fit_p)
plot(fit_p)
pp_check(fit_p)
```

### zero inflated poisson
```{r, message=FALSE}
# zero inflated poisson
fit_zip <- brm(siq_total.T3 ~ 1, data = siq_graph, family = zero_inflated_poisson())
summary(fit_zip)
fit_zip <- add_criterion(fit_zip, c("loo", "kfold", "waic"), reloo = TRUE)
l_fit_zip <- loo(fit_zip, save_psis = TRUE, k_threshold = 0.7)
plot(l_fit_zip, diagnotic="k")
print(l_fit_zip)
plot(fit_zip)
pp_check(fit_zip)
```

### zero inflated negative binomial
```{r, message=FALSE}
# zero inflated binomial
fit_zib <- brm(siq_total.T3 ~ 1, data = siq_graph, family = zero_inflated_negbinomial())
summary(fit_zib)
fit_zib <- add_criterion(fit_zib, c("loo", "kfold", "waic"), reloo = TRUE)
l_fit_zib <- loo(fit_zib, save_psis = TRUE, k_threshold = 0.7)
plot(l_fit_zib, diagnotic="k")
print(l_fit_zib)
plot(fit_zib)
pp_check(fit_zib)
```

### negative binomial
```{r, message=FALSE}
# neg binomial
fit_nb <- brm(siq_total.T3 ~ 1, data = siq_graph, family = negbinomial())
summary(fit_nb)
fit_nb <- add_criterion(fit_nb, c("loo", "kfold", "waic"), reloo = TRUE)
l_fit_nb <- loo(fit_nb, save_psis = TRUE, k_threshold = 0.7)
plot(l_fit_nb, diagnotic="k")
print(l_fit_nb)
plot(fit_nb)
pp_check(fit_nb)
fit_nb$fit
glm.nb(siq_total.T3 ~ 1, data = siq_graph)
```


## Comparing Models  
_widely applicable information criterion (waic)_  
_leave one out (loo)_  
_k-fold cross validation_ 

### comparing poisson and zero inflated poisson (ZIP)
```{r, message=FALSE}
lo_compare_zipandp <- loo_compare(fit_zip, fit_p, criterion = c("loo", "waic", "kfold"))
print(lo_compare_zipandp)
#        elpd_diff se_diff
# fit_zip   0.0       0.0  
# fit_p   -84.5      28.8  

model_weights(fit_zip, fit_p)
#  fit_zip    fit_p 
# 0.5258663 0.4741337 

loo(fit_zip, fit_p)
# looic estimate for fit_zip 1402.6
# looic estimate for fit_p 1570.1

```
Seems like `ZIP` better fit SIQ data because elpd_diff and se_diff was zero compared to `poisson`, and the model weight was slighlty higher for `ZIP` compared to `poisson`.

### comparing ZIP and zero inflated neg binomial (ZIB)
```{r, message=FALSE}
lo_compare_zibandzip <- loo_compare(fit_zib, fit_zip, criterion = c("loo", "waic", "kfold"))

print(lo_compare_zibandzip)
#         elpd_diff se_diff
# fit_zib    0.0       0.0 
# fit_zip -366.3      90.3 

model_weights(fit_zib, fit_zip)
#   fit_zib      fit_zip 
# 1.000000e+00 4.746838e-08  

loo(fit_zib, fit_zip)
```

### comparing ZIB and negative binomial
```{r, message=FALSE}
lo_compare_zibandnb <- loo_compare(fit_nb, fit_zib, criterion = c("loo", "waic", "kfold"))

print(lo_compare_zibandnb)
#         elpd_diff se_diff
# fit_nb   0.0       0.0   
# fit_zib -0.9       0.5  

model_weights(fit_nb, fit_zib)
#       fit_nb      fit_zib 
# 9.999993e-01 7.457582e-07 

loo(fit_nb, fit_zib)
```
Seems like `NB` better fit SIQ data because elpd_diff and se_diff was zero compared to `ZIB`, and the model weight was higher for `NB` compared to `NB`.

# tranforming suicidal ideation data to see if I can use gaussian distribution
```{r}
library(dlookr)
siq_z <- siq_graph %>% 
  mutate(siq_minmax = transform(siq_graph$siq_total.T3, method = "minmax")) %>%
  dplyr::select(siq_minmax) %>% 
  boxplot()

siq_log = transform(siq_graph$siq_total.T3, method = "log+1") # can't do log of 0, so doing log + 1
summary(siq_log)
plot(siq_log)

siq_graph <- siq_graph %>%
  mutate(
    siq_total_log = transform(siq_graph$siq_total.T3, method = "log+1")
  )

siq_responses <- siq_graph %>%
  dplyr::select(ELS_ID, siq_total.T3, siq_total_log)

siq_t3_fp_new <- "~/Box/siq_t3_response.csv"
write_csv(siq_responses, siq_t3_fp_new)
```
The normal distribution looks pretty good.

# data viz
```{r}
sum <- siq_graph %>%
  dplyr::select(ELS_ID, siq_total.T3, siq_total_log) %>%
  summarize(
    siq_mean_log = mean(siq_total_log),
    siq_med_log = median(siq_total_log),
    siq_sd_log = sd(siq_total_log),
    siq_min_log = min(siq_total_log),
    siq_max_log = max(siq_total_log),
    siq_mean = mean(siq_total.T3),
    siq_med = median(siq_total.T3),
    siq_sd = sd(siq_total.T3),
    siq_min = min(siq_total.T3),
    siq_max = max(siq_total.T3)
  )
siq_graph_plot_log <- siq_graph %>% 
 dplyr::select(ELS_ID, siq_total_log) %>%
  ggplot(.,
         aes(x=siq_total_log)) +
  geom_histogram(binwidth = .5, position = "identity", alpha = .5) +
  scale_x_continuous(breaks = seq(from = 0, to = 5, by = 1), 
                     name = "SIQ Scores") +
  scale_y_continuous(breaks = seq(from = 0, to = 20, by = 5)) +
  ggtitle("Distribution of suicidal ideation") +
  theme_light()
ggsave("siq_graph.jpg", siq_graph_plot, width = 7, height = 5)
```

###  gaussian
```{r, message=FALSE}

fit_m <- brm(siq_total_log ~ 1, data = siq_graph, family = gaussian())
summary(fit_m)
fit_m <- add_criterion(fit_m, c("loo", "kfold", "waic"), reloo = TRUE)
l_fit_m <- loo(fit_m, save_psis = TRUE, k_threshold = 0.7)
plot(l_fit_m, diagnotic="k")
print(l_fit_m)
plot(fit_m)
pp_check(fit_m)
```

```{r}
library(tidybayes)

# add_residual_draws() gives us draws from the posterior distribution for each residual:
siq_graph %>%
  add_residual_draws(fit_m) %>%
  ggplot(aes(x = .row, y = .residual)) +
  stat_pointinterval()
```

residual plot
```{r}
# QQ plot:
siq_graph %>%
  add_residual_draws(fit_m) %>%
  median_qi() %>%
  ggplot(aes(sample = .residual)) +
  geom_qq() +
  geom_qq_line()
```

__Summary__
Looks like the log-transformed siq data looks pretty normal. will use this for the lasso.

